---
title: "loo"
output: 
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    code_folding: "hide"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## libraries

```{r}

library(tidyverse)
library(brms)
library(bayesplot)
library(here)
library(scales)

theme_set(theme_light())

source(here("common/brms_model.R"))

```

## data

```{r}

obs_only <- 
  read_csv(here::here("m1_[color_stm_STIM]/data/stimulation_obvs.csv")) %>%
  mutate(subj = as_factor(subj),
         obs_degree = error,
         error = obs_degree * (pi/180))

```

## full model

```{r}

# define prior

bprior <- 
  prior(normal(4, 0.5), class = "b", coef = "intercept", dpar = "circSD") + 
  prior(normal(0, 0.5), class = "b", coef = "stimulation", dpar = "circSD") +
  prior(normal(0, 0.5), class = "sd", coef = "Intercept", dpar = "circSD", group = "subj_index") + 
  prior(normal(0, 0.5), class = "sd", coef = "stimulation", dpar = "circSD", group = "subj_index") + 
  prior(normal(0, 1.5), class = "b", coef = "intercept", dpar = "theta") + 
  prior(normal(0, 1), class = "b", coef = "stimulation", dpar = "theta") +
  prior(normal(0, 1.5), class = "sd", coef = "Intercept", dpar = "theta", group = "subj_index") + 
  prior(normal(0, 1), class = "sd", coef = "stimulation", dpar = "theta", group = "subj_index")


iter = 4000
warmup = 2000
cores = 4
chains = 4
n_post_samples = (iter - warmup) * chains

fit_full <- brm(bform_full, obs_only, family = vm_uniform_mix, prior = bprior, stanvars = stanvars,
                 warmup = warmup, iter = iter, cores = cores, chains = chains, 
                 control = list(adapt_delta = 0.99), inits = 0, 
                 file = "fit_full")

```

### fit check
#### divergences
```{r fig.width=6}

model_fit <- fit_full

#check neff and rhat and divergences
np <- nuts_params(model_fit)
rhat <- brms::rhat(model_fit)
neff_rat <- neff_ratio(model_fit)

np %>% 
  filter(Parameter == "divergent__") %>%
  summarise(n_div = sum(Value))
```

#### rhat
```{r fig.width=6}
mcmc_rhat(rhat) + yaxis_text(hjust = 1) + scale_x_continuous(breaks = pretty_breaks(6))
```

#### neff ratio
```{r fig.width=6}
mcmc_neff(neff_rat) + yaxis_text(hjust = 1)
```

#### trace plots
```{r fig.width=10, fig.height=6}
mcmc_trace(as.array(model_fit$fit))
```


## reduced model: no pre to post change on circSD parameter

```{r}

# define prior

bprior <- 
  prior(normal(4, 0.5), class = "b", coef = "intercept", dpar = "circSD") + 
  #prior(normal(0, 0.5), class = "b", coef = "stimulation", dpar = "circSD") +
  prior(normal(0, 0.5), class = "sd", coef = "Intercept", dpar = "circSD", group = "subj_index") + 
  prior(normal(0, 0.5), class = "sd", coef = "stimulation", dpar = "circSD", group = "subj_index") + 
  prior(normal(0, 1.5), class = "b", coef = "intercept", dpar = "theta") + 
  prior(normal(0, 1), class = "b", coef = "stimulation", dpar = "theta") +
  prior(normal(0, 1.5), class = "sd", coef = "Intercept", dpar = "theta", group = "subj_index") + 
  prior(normal(0, 1), class = "sd", coef = "stimulation", dpar = "theta", group = "subj_index")


iter = 4000
warmup = 2000
cores = 4
chains = 4
n_post_samples = (iter - warmup) * chains

fit_DcircSD_null <- brm(bform_DcircSD_null, obs_only, family = vm_uniform_mix, prior = bprior, stanvars = stanvars,
                 warmup = warmup, iter = iter, cores = cores, chains = chains, 
                 control = list(adapt_delta = 0.99), inits = 0, 
                 file = "fit_DcircSD_null")

```


### fit check
#### divergences
```{r fig.width=6}

model_fit <- fit_DcircSD_null

#check neff and rhat and divergences
np <- nuts_params(model_fit)
rhat <- brms::rhat(model_fit)
neff_rat <- neff_ratio(model_fit)

np %>% 
  filter(Parameter == "divergent__") %>%
  summarise(n_div = sum(Value))
```

#### rhat
```{r fig.width=6}
mcmc_rhat(rhat) + yaxis_text(hjust = 1) + scale_x_continuous(breaks = pretty_breaks(6))
```

#### neff ratio
```{r fig.width=6}
mcmc_neff(neff_rat) + yaxis_text(hjust = 1)
```

#### trace plots
```{r fig.width=10, fig.height=6}
mcmc_trace(as.array(model_fit$fit))
```


## reduced model: no pre to post change on pMem parameter

```{r}

# define prior

bprior <- 
  prior(normal(4, 0.5), class = "b", coef = "intercept", dpar = "circSD") + 
  prior(normal(0, 0.5), class = "b", coef = "stimulation", dpar = "circSD") +
  prior(normal(0, 0.5), class = "sd", coef = "Intercept", dpar = "circSD", group = "subj_index") + 
  prior(normal(0, 0.5), class = "sd", coef = "stimulation", dpar = "circSD", group = "subj_index") + 
  prior(normal(0, 1.5), class = "b", coef = "intercept", dpar = "theta") + 
  #prior(normal(0, 1), class = "b", coef = "stimulation", dpar = "theta") +
  prior(normal(0, 1.5), class = "sd", coef = "Intercept", dpar = "theta", group = "subj_index") + 
  prior(normal(0, 1), class = "sd", coef = "stimulation", dpar = "theta", group = "subj_index")


iter = 4000
warmup = 2000
cores = 4
chains = 4
n_post_samples = (iter - warmup) * chains

fit_DpMem_null <- brm(bform_DpMem_null, obs_only, family = vm_uniform_mix, prior = bprior, stanvars = stanvars,
                 warmup = warmup, iter = iter, cores = cores, chains = chains, 
                 control = list(adapt_delta = 0.99), inits = 0, 
                 file = "fit_DpMem_null")

```

### fit check
#### divergences
```{r fig.width=6}

model_fit <- fit_DpMem_null

#check neff and rhat and divergences
np <- nuts_params(model_fit)
rhat <- brms::rhat(model_fit)
neff_rat <- neff_ratio(model_fit)

np %>% 
  filter(Parameter == "divergent__") %>%
  summarise(n_div = sum(Value))
```

#### rhat
```{r fig.width=6}
mcmc_rhat(rhat) + yaxis_text(hjust = 1) + scale_x_continuous(breaks = pretty_breaks(6))
```

#### neff ratio
```{r fig.width=6}
mcmc_neff(neff_rat) + yaxis_text(hjust = 1)
```

#### trace plots
```{r fig.width=10, fig.height=6}
mcmc_trace(as.array(model_fit$fit))
```


## reduced model: no pre to post change on pMem or circSD parameter

```{r}

# define prior

bprior <- 
  prior(normal(4, 0.5), class = "b", coef = "intercept", dpar = "circSD") + 
  #prior(normal(0, 0.5), class = "b", coef = "stimulation", dpar = "circSD") +
  prior(normal(0, 0.5), class = "sd", coef = "Intercept", dpar = "circSD", group = "subj_index") + 
  prior(normal(0, 0.5), class = "sd", coef = "stimulation", dpar = "circSD", group = "subj_index") + 
  prior(normal(0, 1.5), class = "b", coef = "intercept", dpar = "theta") + 
  #prior(normal(0, 1), class = "b", coef = "stimulation", dpar = "theta") +
  prior(normal(0, 1.5), class = "sd", coef = "Intercept", dpar = "theta", group = "subj_index") + 
  prior(normal(0, 1), class = "sd", coef = "stimulation", dpar = "theta", group = "subj_index")


iter = 4000
warmup = 2000
cores = 4
chains = 4
n_post_samples = (iter - warmup) * chains

fit_DcircSD_DpMem_null <- 
              brm(bform_DcircSD_DpMem_null, obs_only, family = vm_uniform_mix, prior = bprior, stanvars = stanvars,
                 warmup = warmup, iter = iter, cores = cores, chains = chains, 
                 control = list(adapt_delta = 0.99), inits = 0, 
                 file = "fit_DcircSD_DpMem_null")

```

### fit check
#### divergences
```{r fig.width=6}

model_fit <- fit_DcircSD_DpMem_null

#check neff and rhat and divergences
np <- nuts_params(model_fit)
rhat <- brms::rhat(model_fit)
neff_rat <- neff_ratio(model_fit)

np %>% 
  filter(Parameter == "divergent__") %>%
  summarise(n_div = sum(Value))
```

#### rhat
```{r fig.width=6}
mcmc_rhat(rhat) + yaxis_text(hjust = 1) + scale_x_continuous(breaks = pretty_breaks(6))
```

#### neff ratio
```{r fig.width=6}
mcmc_neff(neff_rat) + yaxis_text(hjust = 1)
```

#### trace plots
```{r fig.width=10, fig.height=6}
mcmc_trace(as.array(model_fit$fit))
```

## loo compare

```{r}

#need to do this only once?
expose_functions(fit_full, vectorize = TRUE)

fit_full <- add_loo(fit_full, file = "fit_full")
fit_DcircSD_null <- add_loo(fit_DcircSD_null, file = "fit_DcircSD_null")
fit_DpMem_null <- add_loo(fit_DpMem_null, file = "fit_DpMem_null")
fit_DcircSD_DpMem_null <- add_loo(fit_DcircSD_DpMem_null, file = "fit_DcircSD_DpMem_null")

print("fit_full")
fit_full$loo

print("fit_DcircSD_null")
fit_DcircSD_null$loo

print("fit_DpMem_null")
fit_DpMem_null$loo

print("fit_DcircSD_DpMem_null")
fit_DcircSD_DpMem_null$loo

loo_compare(fit_full, fit_DcircSD_null, fit_DpMem_null, fit_DcircSD_DpMem_null, criterion = "loo")

```

