---
title: "prior_predictive_check"
output: html_document
css: style.css
fig_width: 10 
fig_height: 6
---

### library load

```{r}
library(tidyverse)
library(glue)
library(tidybayes)
library(cowplot)
library(scales)
library(GGally)

theme_set(theme_cowplot())

load_existing_sim <- TRUE
```


I'm starting this prior check with the work I've already done in the sandbox. In those scripts I already got a sense of what weakly informative priors for my starting model might be. In those files, I only did a visual inspection of the prior predictive distribution, not neccesarily including any summary statistics. I also did not do any sort of checks based on the sample size of the small design I have.

### model

Written down the model is:

$$
\begin{aligned}
\mathrm{-likelihood-} \\
error_i &\sim (1-p\_guess_i)*VM(0, \kappa_i) + (p\_guess_i)*Unif(-\pi,\pi) \\
\\
\mathrm{-param~transformation-} \\
\kappa_i &= sd2k(circ\_sd_i) \\
\\
\mathrm{-linear~model-} \\
circ\_sd_i &= exp(\alpha_{0,SUBJ[i]} + \alpha_{\Delta,SUBJ[i]} * postCond) ~~ \mathrm{-log~link~on~sd-} \\
p\_guess_i &= inv\_logit(\beta_{0,SUBJ[i]} + \beta_{\Delta,SUBJ[i]} * postCond) ~~ \mathrm{-logit~link~on~p\_guess-} \\
\\
\mathrm{-priors:~all~independent-}\\
\alpha_{0,SUBJ[...]} &\sim Normal(mu\_\alpha_0, sigma\_\alpha_0) \\
\alpha_{\Delta,SUBJ[...]} &\sim Normal(mu\_\alpha_{\Delta}, sigma\_\alpha_{\Delta}) \\
\beta_{0,SUBJ[...]} &\sim Normal(mu\_\beta_0, sigma\_\beta_0) \\
\beta_{\Delta,SUBJ[...]} &\sim Normal(mu\_\beta_{\Delta}, sigma\_\beta_{\Delta}) \\
\\
mu\_\alpha_0 &\sim Normal(4, 0.5)\\
sigma\_\alpha_0 &\sim Normal^+(0, 0.5) \\
mu\_\alpha_{\Delta} &\sim Normal(0, 0.5)\\
sigma\_\alpha_{\Delta} &\sim Normal^+(0, 0.5)\\
mu\_\beta_0 &\sim Normal(0, 1.5)\\
sigma\_\beta_0 &\sim Normal^+(0, 1.5)\\
mu\_\beta_{\Delta} &\sim Normal(0, 1)\\
sigma\_\beta_{\Delta} &\sim Normal^+(0, 1)\\
\end{aligned}
$$

------

### real obs load

I am considering the color stimulation data. samples sizes:

```{r}

obs_data <- read_csv('../data/stimulation_obvs.csv')

#summarize subj num, obs count, and obs condition split
(subj_summary <- obs_data %>%
  group_by(subj_index) %>%
  summarise(n_obs = n(), frac_stim = mean(stimulation)))


```

2 subjs with 252 observations each, 126 per condition. 

9/12 - I am thinking I should simulate varying effects using the actual samples sizes I have. I also think that this shouldnt matter (at least for a model like this). I'll also try with a larger number of subjects.


------

### Simulation

```{r}

nsubj_sim <- 15
nobs_per_cond_sim <- 126

```


functions

```{r}

# this function takes a single set of parameters and covariates and simlates an observation from the mixture model
simulateData_likelihood <- function(subj_alpha0,
                                    subj_alphaD,
                                    subj_beta0, 
                                    subj_betaD,
                                    stimulation){
  
    # calculate the delinked mixing proportion
    pMem_linked <- subj_beta0 + (subj_betaD * stimulation)
    pMem <- exp(pMem_linked)/(1 + exp(pMem_linked))
  
    # which part of the mixture does this obs come from
    memFlip <- rbernoulli(1, pMem)
    
    obs <- NA
    
    if (memFlip == 1){
      obs <- Rfast::rvonmises(1, pi, exp(subj_alpha0 + (subj_alphaD*stimulation))) - pi
    }else{    
      obs <- runif(1, -pi, pi)
    }
    
    obs_tibble <- tibble(obs_radian = obs, obs_degree = pracma::rad2deg(obs))
    
    return(obs_tibble)   
  
}

simulateData_subj <- function(subj_alpha0, subj_alphaD, subj_beta0, subj_betaD, nobs_per_condition){
  
    conditions <- c(0,1)
    
    subj_data <- tibble(
      subj_alpha0 = subj_alpha0,
      subj_alphaD = subj_alphaD,
      subj_beta0 = subj_beta0,
      subj_betaD = subj_betaD,
      stimulation = rep(conditions, each = nobs_per_condition)
    )
  
    subj_data <- subj_data %>% 
      mutate(subj_obs = pmap(subj_data, simulateData_likelihood)) %>%
      select(-c(subj_alpha0, subj_alphaD, subj_beta0, subj_betaD)) %>%
      unnest(subj_obs)
    
    return(subj_data)
}

# this function will take a single set of simulated parameter draws and then simulate an implied data set
simulateData <- function(sim_num, 
                         alpha0_mu, alpha0_sigma,
                         alphaD_mu, alphaD_sigma,
                         beta0_mu, beta0_sigma,
                         betaD_mu, betaD_sigma,
                         nsubj = 100, nobs_per_condition = 100){
  
  print(glue("simulation: {sim_num}"))
  
  # generate lower level subject-specific parameters
  sim_subj_alpha0 <- rnorm(nsubj, alpha0_mu, alpha0_sigma)
  sim_subj_alphaD <- rnorm(nsubj, alphaD_mu, alphaD_sigma)
  
  sim_subj_beta0 <- rnorm(nsubj, beta0_mu, beta0_sigma)
  sim_subj_betaD <- rnorm(nsubj, betaD_mu, betaD_sigma)
  
  sim_data <- tibble(
         subj = 1:nsubj,
         subj_alpha0 = sim_subj_alpha0,
         subj_alphaD = sim_subj_alphaD,
         subj_beta0 = sim_subj_beta0,
         subj_betaD = sim_subj_betaD,
         nobs_per_condition = nobs_per_condition
         )
  
  sim_data <- sim_data %>% 
    mutate(subj_obs = pmap(sim_data %>% select(-subj), simulateData_subj))
  
  return(sim_data)
}


  
```

run simulate

```{r}

found_existing_sim <- FALSE
if (file.exists("sim_datasets.rds")){
  found_existing_sim <- TRUE
}


if (load_existing_sim == FALSE || found_existing_sim == FALSE){

  nsim_datasets <- 1000
  
  sim_priors <- tibble(
    sim_num = 1:nsim_datasets,
    alpha0_mu = rnorm(nsim_datasets, 4, 0.5),
    alpha0_sigma = abs(rnorm(nsim_datasets, 0, 0.5)),
    alphaD_mu =  rnorm(nsim_datasets, 0, 0.5),
    alphaD_sigma = abs(rnorm(nsim_datasets, 0, 0.5)),
    beta0_mu = rnorm(nsim_datasets, 0, 1.5),
    beta0_sigma = abs(rnorm(nsim_datasets, 0, 1.5)),
    betaD_mu = rnorm(nsim_datasets, 0, 1),
    betaD_sigma = abs(rnorm(nsim_datasets, 0, 1)),
    nsubj = nsubj_sim,
    nobs_per_cond = nobs_per_cond_sim
  )
  
  sim_datasets <- sim_priors %>%
    mutate(dataset = pmap(sim_priors, simulateData))
  
  saveRDS(sim_datasets, file = "sim_datasets.rds")

}else{
  
  sim_datasets <- readRDS("sim_datasets.rds")
}

```

Check sim data

```{r}
head(sim_datasets)
```

```{r}
head(sim_datasets$dataset[[1]])
```

```{r}
head(sim_datasets$dataset[[1]]$subj_obs[[1]])
```


------

### Plot distributions and summary statistics

Ideas:

Definitely plot the priors on the intercept and slope means, transformed back into sd 

plot the prior predicitive densities for subjects

Some other plot ideas:

shaded histogram plot, combining data across stimulation conditions - check if data looks too peaked or too flat

shaded histogram plot, one for each stimulation condition - same check ^

plot of density lines, one from each sim dataset, one with both conditions and one with them split out - this would help identify weird distribution more that shaded histogram perhaps

#### Sanity checks that prior samples are drawn correctly

```{r fig.width=10, fig.height=6}

sim_datasets %>%
  select(alpha0_mu, alpha0_sigma, alphaD_mu, alphaD_sigma) %>%
  ggpairs(progress = FALSE)

```
Good. 

```{r fig.width=10, fig.height=6}

sim_datasets %>%
  select(beta0_mu, beta0_sigma, betaD_mu, betaD_sigma) %>%
  ggpairs(progress = FALSE)

```

Good.

### Prior distribution on von-mises circSD, linear model parameters (pre group mean, post group mean, post-pre mean change)

No accounting for subject variance here

```{r, fig.width=10, fig.height=6}

##
## alpha0_mu 
##

## linked prior distribution
alpha0_mu_hist <- sim_datasets %>%
  ggplot(aes(x = alpha0_mu)) + 
  geom_histogram(binwidth = 0.05, fill = "#F16C66") +
  theme(legend.position = "none",
        axis.title = element_text(size = 12),
        plot.title = element_text(size = 12)) + 
  labs(x = "linked prior on group mean for circSD, pre condition",
       title = "circSD group mean prior, alpha0_mu") + 
  scale_x_continuous(limits = c(1,7))
  

##
## alpha0_mu + alphaD_mu = alpha1_mu 
##

## linked prior distribution
alpha1_mu_hist <- sim_datasets %>%
  transmute(alpha1_mu = alpha0_mu + alphaD_mu) %>%
  ggplot(aes(x = alpha1_mu)) + 
  geom_histogram(binwidth = 0.05, fill = "#685369") +
  theme(axis.title = element_text(size = 12),
        plot.title = element_text(size = 12)) +
  labs(x = "linked prior on group mean for circSD, post condition",
       title = "circSD group mean prior, alpha0_mu + alphaD_mu") + 
  scale_x_continuous(limits = c(1,7))


plot_grid(alpha0_mu_hist, alpha1_mu_hist, nrow = 1, align = "h")

```


```{r fig.width=10, fig.height=6}

##
## alpha0_mu 
##

## delinked prior alpha0_mu
alpha0_mu_delinked_stats <- sim_datasets %>%
  transmute(delinked = exp(alpha0_mu)) %>%
  summarise(less_than_5 = sum(delinked < 5)/n(), greater_than_120 = sum(delinked > 120)/n())

alpha0_mu_delinked_hist <- sim_datasets %>%
  transmute(delinked = exp(alpha0_mu)) %>%
  ggplot(aes(x = delinked)) +
  geom_histogram(binwidth = 2, fill = "#F16C66") + 
  geom_vline(xintercept = c(5, 120), linetype = "dashed") + 
  labs(x = "prior on group mean for circSD, pre condition",
       title = "circSD group mean prior, exp(alpha0_mu)",
       subtitle = glue("prob(circSD < 5) = {alpha0_mu_delinked_stats$less_than_5}\nprob(circSD > 120) = {alpha0_mu_delinked_stats$greater_than_120}")) + 
  theme(axis.title = element_text(size = 12),
        plot.title = element_text(size = 12)) 
  
##
## alpha0_mu + alphaD_mu = alpha1_mu 
##  
  
## delinked prior alpha0_mu + alphaD_mu
alpha1_mu_delinked_hist <- sim_datasets %>%
  transmute(delinked = exp(alpha0_mu + alphaD_mu)) %>%
  ggplot(aes(x = delinked)) + 
  geom_histogram(binwidth = 2, fill = "#685369") + 
  labs(x = "prior on group mean for circSD, post condition",
       title = "circSD group mean prior, exp(alpha0_mu + alphaD_mu)") + 
  theme(axis.title = element_text(size = 12),
        plot.title = element_text(size = 12))


plot_grid(alpha0_mu_delinked_hist, alpha1_mu_delinked_hist, nrow = 1, align = "h")
```

```{r fig.width=10, fig.height=6}

##
## exp(alpha0_mu + alphaD_mu) - exp(alpha0_mu) plot
##

alphaD_mu_delinked_stats <- sim_datasets %>%
  transmute(delinked = exp(alpha0_mu + alphaD_mu) - exp(alpha0_mu)) %>%
  summarise(less_than_n100 = sum(delinked < -100)/n(), greater_than_100 = sum(delinked > 100)/n())

alphaD_mu_delinked_hist <- sim_datasets %>%
  transmute(delinked = exp(alpha0_mu + alphaD_mu) - exp(alpha0_mu)) %>%
  ggplot(aes(x = delinked)) + 
  geom_histogram(binwidth = 2, fill = "#00AEB2") + 
  geom_vline(xintercept = c(-100, 100), linetype = "dashed") + 
  labs(x = "prior on group mean for delta-circSD, mean post minus mean pre",
       title = "delta-circSD group mean prior, exp(alpha0_mu + alphaD_mu) - exp(alpha0_mu)",
       subtitle = glue("prob(delta-circSD < -100) = {alphaD_mu_delinked_stats$less_than_n100}\nprob(delta-circSD > 100) = {alphaD_mu_delinked_stats$greater_than_100}")) + 
  theme(axis.title = element_text(size = 12),
        plot.title = element_text(size = 12)) + 
  scale_x_continuous(breaks= pretty_breaks(10))

alphaD_mu_delinked_hist
```

All these for the prior on circSD mean parameters look good.

### Prior predicitive distribution on subject effects on circSD (based on simulated subjects from each dataset)

These plots indicate the effects of the priors on `alpha0_mu`, `alpha0_sigma`, `alphaD_mu`, `alphaD_sigma`.

```{r eval=FALSE}


sim_subj_circSD_hist_count <- function(dataset, max_val = 120){
  
  pre_circSD <- exp(dataset$subj_alpha0)
  post_circSD <- exp(dataset$subj_alpha0 + dataset$subj_alphaD)
  
  pre_circSD[pre_circSD > max_val] <- max_val
  post_circSD[post_circSD > max_val] <- max_val
  
  breaks <- seq(0, ceiling(max(c(pre_circSD, post_circSD)) / 10 ) * 10 ,10)
  
  pre_circSD_bincount <- hist(pre_circSD, breaks = breaks, plot = FALSE)$counts
  post_circSD_bincount <- hist(post_circSD, breaks = breaks, plot = FALSE)$counts
  
  pre_circSD_bincount_names <- glue("pre_circSD_c{breaks[-1]}")
  post_circSD_bincount_names <- glue("post_circSD_c{breaks[-1]}")
  
  bincounts <- tibble(ct = c(pre_circSD_bincount, post_circSD_bincount), 
                      ct_name = c(pre_circSD_bincount_names, post_circSD_bincount_names))

  return(bincounts)
  
}


sim_datasets %>% 
  select(sim_num, dataset) %>%
  mutate(subj_hist_counts = map(dataset, sim_subj_circSD_hist_count)) %>% 
  unnest(subj_hist_counts) %>% 
  pivot_wider(names_from = ct_name, values_from = ct) %>%
  replace(is.na(.), 0) %>% head()
  select(-c(sim_num, dataset)) %>%
  mutate(quants = map(everything(), ~quantile(., probs = seq(0.1, 0.9, 0.1)))) %>%
  unnest(quants) %>% head
  
```


##### Marginal prior on subjects pre circSD, post circSD, and effect size (ignoring simulation sample sizes)


```{r}

sim_datasets_unnest <- sim_datasets %>%
  unnest(dataset) %>%
  mutate(alpha0_mu_delinked = exp(alpha0_mu),
         alpha1_mu_delinked = exp(alpha0_mu + alphaD_mu),
         subj_pre_circSD = exp(subj_alpha0),
         subj_post_circSD = exp(subj_alphaD + subj_alpha0),
         subj_circSD_ES = subj_post_circSD - subj_pre_circSD) 

```

```{r fig.width=10, fig.height=6}
 
subj_pre_circSD_plot <- sim_datasets_unnest %>%
  mutate(subj_pre_circSD = if_else(subj_pre_circSD > 120, 120, subj_pre_circSD)) %>%
  ggplot(aes(x = subj_pre_circSD)) + 
  geom_histogram(binwidth = 5, fill = "red", alpha = 0.3) + 
  labs(x = "subj_pre_circSD [prior predictive distribution]",
       subtitle = glue("p(<5) = {sum(sim_datasets_unnest$subj_pre_circSD < 5)/length(sim_datasets_unnest$subj_pre_circSD)}\n p(>120) = {sum(sim_datasets_unnest$subj_pre_circSD > 120)/length(sim_datasets_unnest$subj_pre_circSD)}"))


subj_post_circSD_plot <- sim_datasets_unnest %>%
  mutate(subj_post_circSD = if_else(subj_post_circSD > 120, 120, subj_post_circSD)) %>%
  ggplot(aes(x = subj_post_circSD)) + 
  geom_histogram(binwidth = 5, fill = "red", alpha = 0.3) + 
  labs(x = "subj_post_circSD [prior predictive distribution]",
       subtitle = glue("p(<5) = {sum(sim_datasets_unnest$subj_post_circSD < 5)/length(sim_datasets_unnest$subj_post_circSD)}\n p(>120) = {sum(sim_datasets_unnest$subj_post_circSD > 120)/length(sim_datasets_unnest$subj_post_circSD)}"))


subj_circSD_ES_plot <- sim_datasets_unnest %>%
  mutate(subj_circSD_ES = if_else(subj_circSD_ES > 100, 100, subj_circSD_ES)) %>%
  mutate(subj_circSD_ES = if_else(subj_circSD_ES < -100, -100, subj_circSD_ES)) %>%
  ggplot(aes(x = subj_circSD_ES)) + 
  geom_histogram(binwidth = 5, fill = "red", alpha = 0.7) + 
  labs(x = "subj_circSD_ES [prior predictive distribution]",
       subtitle = glue("p(< -100) = {sum(sim_datasets_unnest$subj_circSD_ES < -100)/length(sim_datasets_unnest$subj_circSD_ES)}\n p(>100) = {sum(sim_datasets_unnest$subj_circSD_ES > 100)/length(sim_datasets_unnest$subj_circSD_ES)}"))

plot_grid(subj_pre_circSD_plot, subj_post_circSD_plot, subj_circSD_ES_plot, ncol = 1)

```




Calculate min and max subject pre, post, and circSD effect size in each simulation.

```{r}
sim_subj_extremes <- sim_datasets %>% 
  unnest(dataset) %>%
  mutate(subj_alpha1 = subj_alpha0 + subj_alphaD, 
         subj_alpha0_delinked = exp(subj_alpha0), 
         subj_alpha1_delinked = exp(subj_alpha1), 
         subj_circSD_effect = subj_alpha1_delinked - subj_alpha0_delinked ) %>%
  group_by(sim_num) %>%
  summarize_at(vars(subj_alpha0_delinked, subj_alpha1_delinked, subj_circSD_effect), list(max = max, min = min)) 

```


##### Across-sim max pre condition circSD

```{r fig.width=10, fig.height=6}

#What is the max subject pre condition value in each dataset
pre_plot <- sim_subj_extremes %>%
  mutate(subj_alpha0_delinked_max = if_else(subj_alpha0_delinked_max > 120, 120, subj_alpha0_delinked_max)) %>%
  ggplot() + 
  geom_histogram(aes(x = subj_alpha0_delinked_max, fill = "red", alpha = 0.3), binwidth = 5) +
  theme(legend.position = "none") + 
  labs(x = "pre condition: max subj circSD per sim [subj_alpha0_delinked_max]",
       subtitle = glue("p(<5) = {sum(sim_subj_extremes$subj_alpha0_delinked_max < 5)/length(sim_subj_extremes$subj_alpha0_delinked_max)}\n p(>120) = {sum(sim_subj_extremes$subj_alpha0_delinked_max > 120)/length(sim_subj_extremes$subj_alpha0_delinked_max)}"))

#What is the max subject post condition value in each dataset
post_plot <- sim_subj_extremes %>%
  mutate(subj_alpha1_delinked_max = if_else(subj_alpha1_delinked_max > 120, 120, subj_alpha1_delinked_max)) %>%
  ggplot() + 
  geom_histogram(aes(x = subj_alpha1_delinked_max, fill = "red", alpha = 0.3), binwidth = 5) + 
  theme(legend.position = "none") + 
  labs(x = "post condition: max subj circSD per sim [subj_alpha1_delinked_max]",
       subtitle = glue("p(<5) = {sum(sim_subj_extremes$subj_alpha1_delinked_max < 5)/length(sim_subj_extremes$subj_alpha1_delinked_max)}\n p(>120) = {sum(sim_subj_extremes$subj_alpha1_delinked_max > 120)/length(sim_subj_extremes$subj_alpha1_delinked_max)}"))


plot_grid(pre_plot, post_plot, ncol =1, align = 'v')

```

This looks horrible. circSD should rarely go above 120.

##### Across-sim min pre condition circSD

```{r fig.width=10, fig.height=6}

pre_plot <- sim_subj_extremes %>%
  mutate(subj_alpha0_delinked_min = if_else(subj_alpha0_delinked_min > 120, 120, subj_alpha0_delinked_min)) %>%
  ggplot() + 
  geom_histogram(aes(x = subj_alpha0_delinked_min, fill = "red", alpha = 0.3), binwidth = 5) +
  theme(legend.position = "none") + 
  labs(x = "pre condition: min subj circSD per sim [subj_alpha0_delinked_min]",
       subtitle = glue("p(<5) = {sum(sim_subj_extremes$subj_alpha0_delinked_min < 5)/length(sim_subj_extremes$subj_alpha0_delinked_min)}\n p(>120) = {sum(sim_subj_extremes$subj_alpha0_delinked_min > 120)/length(sim_subj_extremes$subj_alpha0_delinked_min)}"))

#What is the most extreme subject post condition value in each dataset
post_plot <- sim_subj_extremes %>%
  mutate(subj_alpha1_delinked_min = if_else(subj_alpha1_delinked_min > 120, 120, subj_alpha1_delinked_min)) %>%
  ggplot() + 
  geom_histogram(aes(x = subj_alpha1_delinked_min, fill = "red", alpha = 0.3), binwidth = 5) + 
  theme(legend.position = "none") + 
  labs(x = "post condition: min subj circSD per sim [subj_alpha1_delinked_min]",
       subtitle = glue("p(<5) = {sum(sim_subj_extremes$subj_alpha1_delinked_min < 5)/length(sim_subj_extremes$subj_alpha1_delinked_min)}\n p(>120) = {sum(sim_subj_extremes$subj_alpha1_delinked_min > 120)/length(sim_subj_extremes$subj_alpha1_delinked_min)}"))


plot_grid(pre_plot, post_plot, ncol =1, align = 'v')
```

Things look OK from this point of view.

##### Across-sim max+min circSD effect size

```{r fig.width=10, fig.height=6}
#What is the most extreme change from pre to post in a subject

min_plot <- sim_subj_extremes %>%
  mutate(subj_circSD_effect_min = if_else(subj_circSD_effect_min > 100 , 100, subj_circSD_effect_min)) %>%
  mutate(subj_circSD_effect_min = if_else(subj_circSD_effect_min < -100 , -100, subj_circSD_effect_min)) %>%
  ggplot() + 
  geom_histogram(aes(x = subj_circSD_effect_min, fill = "red", alpha = 0.3), binwidth = 5) +
  theme(legend.position = "none") + 
  labs(x = "min subj circSD effect per sim \n[min(subj_alpha1_delinked - subj_alpha0_delinked)]",
       subtitle = glue("p(<-100) = {sum(sim_subj_extremes$subj_circSD_effect_min < -100)/length(sim_subj_extremes$subj_circSD_effect_min)}\n p(>100) = {sum(sim_subj_extremes$subj_circSD_effect_min > 100)/length(sim_subj_extremes$subj_circSD_effect_min)}"))

#What is the most extreme subject post condition value in each dataset
max_plot <- sim_subj_extremes %>%
  mutate(subj_circSD_effect_max = if_else(subj_circSD_effect_max > 100 , 100, subj_circSD_effect_max)) %>%
  mutate(subj_circSD_effect_max = if_else(subj_circSD_effect_max < -100 , -100, subj_circSD_effect_max)) %>%
  ggplot() + 
  geom_histogram(aes(x = subj_circSD_effect_max, fill = "red", alpha = 0.3), binwidth = 5) +
  theme(legend.position = "none") + 
  labs(x = "max subj circSD effect per sim \n[max(subj_alpha1_delinked - subj_alpha0_delinked)]",
       subtitle = glue("p(<-100) = {sum(sim_subj_extremes$subj_circSD_effect_max < -100)/length(sim_subj_extremes$subj_circSD_effect_max)}\n p(>100) = {sum(sim_subj_extremes$subj_circSD_effect_max > 100)/length(sim_subj_extremes$subj_circSD_effect_max)}"))

plot_grid(min_plot, max_plot, ncol =1, align = 'v')


```

Also bad. too many small min effects and too many big max effects. 

-------

##### Dig deeper on circSD priors

Both the max pre/post subject distributions of circSD and the max/min subject effect size distributions on circSD contained too many extreme values.

Can I see which prior distributions I need to change in order to correct these by plotting the points from those distributions along with their respective prior distribution samples?

(Is this a useful technique in general?)

Plots:

for (max pre circSD, max post circSD, max circSD ES, min circSD ES)
*  vs alpha0_mu
*  vs alpha0_sigma
*  vs alphaD_mu
*  vs alphaD_sigma

```{r}

sim_datasets_join_extremes <- sim_datasets %>%
  mutate(alpha0_mu_delinked = exp(alpha0_mu),
         alpha1_mu_delinked = exp(alpha0_mu + alphaD_mu)) %>% 
  left_join(sim_subj_extremes, by = "sim_num")


```

```{r fig.width=10, fig.height=6}

#parameters describing uncertanity over group circ SDs in the pre condition (alpha0_mu, alpha0_sigma) 
#vs 
#implied pre condition min and max circSDs

preMax_vs_alpha0_mu <- 
  ggplot(sim_datasets_join_extremes, aes(x = subj_alpha0_delinked_max, y = alpha0_mu_delinked)) + 
  geom_point() + 
  scale_x_continuous(limits = c(0, 200))

preMin_vs_alpha0_mu <- 
  ggplot(sim_datasets_join_extremes, aes(x = subj_alpha0_delinked_min, y = alpha0_mu_delinked)) + 
  geom_point() + 
  scale_x_continuous(limits = c(0, 200))  

preMax_vs_alpha0_sigma <- 
  ggplot(sim_datasets_join_extremes, aes(x = subj_alpha0_delinked_max, y = alpha0_sigma)) + 
  geom_point() + 
  scale_x_continuous(limits = c(0, 200))

preMin_vs_alpha0_sigma <- 
  ggplot(sim_datasets_join_extremes, aes(x = subj_alpha0_delinked_min, y = alpha0_sigma)) + 
  geom_point() + 
  scale_x_continuous(limits = c(0, 200))

plot_grid(preMin_vs_alpha0_mu, preMax_vs_alpha0_mu, preMin_vs_alpha0_sigma, preMax_vs_alpha0_sigma, nrow = 2, align = "hv")

```

```{r fig.width=10, fig.height=6}

#parameters describing uncertanity over change from pre to post condition (alphaD_mu, alphaD_sigma) 
#vs 
#implied post condition min and max circSDs

postMin_vs_alphaD_mu <- 
  ggplot(sim_datasets_join_extremes, aes(x = subj_alpha1_delinked_min, y = alphaD_mu)) + 
  geom_point() + 
  scale_x_continuous(limits = c(0, 200))

postMax_vs_alphaD_mu <- 
  ggplot(sim_datasets_join_extremes, aes(x = subj_alpha1_delinked_max, y = alphaD_mu)) + 
  geom_point() + 
  scale_x_continuous(limits = c(0, 200))  

postMin_vs_alphaD_sigma <- 
  ggplot(sim_datasets_join_extremes, aes(x = subj_alpha1_delinked_min, y = alphaD_sigma)) + 
  geom_point() + 
  scale_x_continuous(limits = c(0, 200))

postMax_vs_alphaD_sigma <- 
  ggplot(sim_datasets_join_extremes, aes(x = subj_alpha1_delinked_max, y = alphaD_sigma)) + 
  geom_point() + 
  scale_x_continuous(limits = c(0, 200))

plot_grid(postMin_vs_alphaD_mu, postMax_vs_alphaD_mu, postMin_vs_alphaD_sigma, postMax_vs_alphaD_sigma, nrow = 2, align = "hv")

```

```{r fig.width=10, fig.height=6}

#parameters describing uncertanity over group circ SDs in the pre condition (alpha0_mu, alpha0_sigma) 
#vs 
#implied effect size min and max

ESmin_vs_alpha0_mu <- 
  ggplot(sim_datasets_join_extremes, aes(x = subj_circSD_effect_min, y = alpha0_mu_delinked)) + 
  geom_point() + 
  scale_x_continuous(limits = c(-100, 100))

ESmax_vs_alpha0_mu <- 
  ggplot(sim_datasets_join_extremes, aes(x = subj_circSD_effect_max, y = alpha0_mu_delinked)) + 
  geom_point() + 
  scale_x_continuous(limits = c(-100, 100))  

ESmin_vs_alpha0_sigma <- 
  ggplot(sim_datasets_join_extremes, aes(x = subj_circSD_effect_min, y = alpha0_sigma)) + 
  geom_point() + 
  scale_x_continuous(limits = c(-100, 100))

ESmax_vs_alpha0_sigma <- 
  ggplot(sim_datasets_join_extremes, aes(x = subj_circSD_effect_max, y = alpha0_sigma)) + 
  geom_point() + 
  scale_x_continuous(limits = c(-100, 100))

plot_grid(ESmin_vs_alpha0_mu, ESmax_vs_alpha0_mu, ESmin_vs_alpha0_sigma, ESmax_vs_alpha0_sigma, nrow = 2, align = "hv")

```



```{r fig.width=10, fig.height=6}

#parameters describing uncertanity over change from pre to post condition(alphaD_mu, alphaD_sigma) 
#vs 
#implied effect size min and max

ESmin_vs_alphaD_mu <- 
  ggplot(sim_datasets_join_extremes, aes(x = subj_circSD_effect_min, y = alphaD_mu)) + 
  geom_point() + 
  scale_x_continuous(limits = c(-100, 100))

ESmax_vs_alphaD_mu <- 
  ggplot(sim_datasets_join_extremes, aes(x = subj_circSD_effect_max, y = alphaD_mu)) + 
  geom_point() + 
  scale_x_continuous(limits = c(-100, 100))  

ESmin_vs_alphaD_sigma <- 
  ggplot(sim_datasets_join_extremes, aes(x = subj_circSD_effect_min, y = alphaD_sigma)) + 
  geom_point() + 
  scale_x_continuous(limits = c(-100, 100))

ESmax_vs_alphaD_sigma <- 
  ggplot(sim_datasets_join_extremes, aes(x = subj_circSD_effect_max, y = alphaD_sigma)) + 
  geom_point() + 
  scale_x_continuous(limits = c(-100, 100))

plot_grid(ESmin_vs_alphaD_mu, ESmax_vs_alphaD_mu, ESmin_vs_alphaD_sigma, ESmax_vs_alphaD_sigma, nrow = 2, align = "hv")

```


Takeaways:

Unsurprisingly, effect size and pre,post extreme values would likely be better contained with narrower priors.

First ideas:

*Only narrow priors on mu parameters, alpha0_mu and alphaD_mu. This should help but the next step will likely be ncessary?

*Also narrow priors on the SD parameters, alpha0_sigma and alphaD_sigma.

### Prior distribution on mixture probability pMem, linear model parameters (pre group mean, post group mean, post-pre mean change)


```{r fig.width=10, fig.height=6}

## linked prior distribution


plot_grid(
  
  sim_datasets %>%
  ggplot(aes(x = beta0_mu)) + 
  geom_histogram(binwidth = 0.05, fill = "#F16C66") +
  theme(legend.position = "none",
        axis.title = element_text(size = 12),
        plot.title = element_text(size = 12)) + 
  labs(x = "linked prior on group mean for pMem, pre condition",
       title = "pMem group mean prior, beta0_mu") + 
  scale_x_continuous(limits = c(-5,5))
  
  ,
  
  sim_datasets %>%
  transmute(beta1_mu = beta0_mu + betaD_mu) %>%
  ggplot(aes(x = beta1_mu)) + 
  geom_histogram(binwidth = 0.05, fill = "#685369") +
  theme(axis.title = element_text(size = 12),
        plot.title = element_text(size = 12)) +
  labs(x = "linked prior on group mean for pMem, post condition",
       title = "pMem group mean prior, beta0_mu + betaD_mu") + 
  scale_x_continuous(limits = c(-5,5))
  
  ,
  
  nrow = 1,
  align = "h"
)

```

```{r fig.width=10, fig.height=6}

##
## inv_logit(beta0_mu)
##

##
## inv_logit(beta0_mu + betaD_mu) = inv_logit(beta1_mu) 
##  

## delinked prior alpha0_mu
beta0_mu_delinked_stats <- sim_datasets %>%
  transmute(delinked = exp(beta0_mu)/(exp(beta0_mu) + 1)) %>%
  summarise(less_than_5 = sum(delinked < 0.05)/n(), greater_than_95 = sum(delinked > 0.95)/n())

plot_grid(
  
  sim_datasets %>%
  transmute(delinked = exp(beta0_mu)/(exp(beta0_mu) + 1)) %>%
  ggplot(aes(x = delinked)) +
  geom_histogram(binwidth = 0.03, fill = "#F16C66") + 
  geom_vline(xintercept = c(0.05, 0.95), linetype = "dashed") + 
  labs(x = "prior on group mean for pMem, pre condition",
       title = "pMem group mean prior, inv_logit(beta0_mu)",
       subtitle = glue("prob(pMem < 0.05) = {beta0_mu_delinked_stats$less_than_5}\nprob(pMem > 0.95) = {beta0_mu_delinked_stats$greater_than_95}")) + 
  theme(axis.title = element_text(size = 12),
        plot.title = element_text(size = 12))
  
  ,
  
  sim_datasets %>%
  transmute(delinked = exp(beta0_mu + betaD_mu)/(exp(beta0_mu + betaD_mu) + 1)) %>%
  ggplot(aes(x = delinked)) + 
  geom_histogram(binwidth = 0.03, fill = "#685369") + 
  labs(x = "prior on group mean for pMem, post condition",
       title = "pMem group mean prior, inv_logit(alpha0_mu + alphaD_mu)") + 
  theme(axis.title = element_text(size = 12),
        plot.title = element_text(size = 12))
  
  ,
  
  nrow = 1,
  align = "h"
)
```


```{r fig.width=10, fig.height=6}

##
## inv_logit(beta0_mu + betaD_mu) - inv_logit(beta0_mu) plot
##

betaD_mu_delinked_stats <- sim_datasets %>%
  transmute(delinked = exp(beta0_mu + betaD_mu)/(exp(beta0_mu + betaD_mu) + 1) - exp(beta0_mu)/(exp(beta0_mu) + 1)) %>%
  summarise(less_than_n80 = sum(delinked < -0.8)/n(), greater_than_80 = sum(delinked > 0.8)/n())

sim_datasets %>%
  transmute(delinked = exp(beta0_mu + betaD_mu)/(exp(beta0_mu + betaD_mu) + 1) - exp(beta0_mu)/(exp(beta0_mu) + 1)) %>%
  ggplot(aes(x = delinked)) + 
  geom_histogram(binwidth = 0.02, fill = "#00AEB2") + 
  geom_vline(xintercept = c(-0.8, 0.8), linetype = "dashed") + 
  labs(x = "prior on group mean for delta-pMem, mean post minus mean pre",
       title = "delta-pMem group mean prior, inv_logit(beta0_mu + betaD_mu) - inv_logit(beta0_mu)",
       subtitle = glue("prob(delta-pMem < -0.8) = {betaD_mu_delinked_stats$less_than_n80}\nprob(delta-pMem > 0.8) = {betaD_mu_delinked_stats$greater_than_80}")) + 
  theme(axis.title = element_text(size = 12),
        plot.title = element_text(size = 12)) + 
  scale_x_continuous(breaks= pretty_breaks(10))

```

### Prior predicitive distribution on subject effects on pMem (based on simulated subjects from each dataset)

##### Marginal prior on subjects pre circSD, post circSD, and effect size (ignoring simulation sample sizes)

```{r}

sim_datasets_unnest <- sim_datasets %>%
  unnest(dataset) %>%
  mutate(beta0_mu_delinked = exp(beta0_mu)/(exp(beta0_mu) + 1),
         beta1_mu_delinked = exp(beta0_mu + betaD_mu)/(exp(beta0_mu + betaD_mu) + 1),
         subj_pre_pMem = exp(subj_beta0)/(exp(subj_beta0) + 1),
         subj_post_pMem = exp(subj_betaD + subj_beta0)/(exp(subj_betaD + subj_beta0) + 1),
         subj_pMem_ES = subj_post_pMem - subj_pre_pMem) 

```

```{r fig.width=10, fig.height=6}

pMem_ES_quantiles <- quantile(sim_datasets_unnest$subj_pMem_ES, c(0.05, 0.95))

plot_grid(
  
  sim_datasets_unnest %>%
  ggplot(aes(x = subj_pre_pMem)) + 
  geom_histogram(binwidth = 0.01, fill = "red", alpha = 0.3) + 
  labs(x = "subj_pre_pMem [prior predictive distribution]",
       subtitle = glue("p(< 0.05) = {sum(sim_datasets_unnest$subj_pre_pMem < 0.05)/length(sim_datasets_unnest$subj_pre_pMem)}\n p(> 0.95) = {sum(sim_datasets_unnest$subj_pre_pMem > 0.95)/length(sim_datasets_unnest$subj_pre_pMem)}"))
  
  ,
  
  sim_datasets_unnest %>%
  ggplot(aes(x = subj_post_pMem)) + 
  geom_histogram(binwidth = 0.01, fill = "red", alpha = 0.3) + 
  labs(x = "subj_post_pMem [prior predictive distribution]",
       subtitle = glue("p(< 0.05) = {sum(sim_datasets_unnest$subj_post_pMem < 0.05)/length(sim_datasets_unnest$subj_post_pMem)}\n p(> 0.95) = {sum(sim_datasets_unnest$subj_post_pMem > 0.95)/length(sim_datasets_unnest$subj_post_pMem)}"))
  
  ,
  
  sim_datasets_unnest %>%
  ggplot(aes(x = subj_pMem_ES)) + 
  geom_histogram(binwidth = 0.01, fill = "red", alpha = 0.7) + 
  geom_vline(xintercept = pMem_ES_quantiles, linetype = "dashed") + 
  labs(x = "subj_pMem_ES [prior predictive distribution], (5%, 95%) quantile lines",
       subtitle = glue("p(< -0.8) = {sum(sim_datasets_unnest$subj_pMem_ES < -0.8)/length(sim_datasets_unnest$subj_pMem_ES)}\n p(> 0.8) = {sum(sim_datasets_unnest$subj_pMem_ES > 0.80)/length(sim_datasets_unnest$subj_pMem_ES)}"))
  
  ,
  
  ncol = 1
)
```

Calculate min and max subject pre, post, and pMem effect size in each simulation.

```{r}

sim_subj_extremes <- sim_datasets %>% 
  unnest(dataset) %>%
  mutate(subj_beta1 = subj_beta0 + subj_betaD, 
         subj_beta0_delinked = exp(subj_beta0)/(exp(subj_beta0) + 1), 
         subj_beta1_delinked = exp(subj_beta0 + subj_betaD)/(exp(subj_beta0 + subj_betaD) + 1), 
         subj_pMem_effect = subj_beta1_delinked - subj_beta0_delinked ) %>%
  group_by(sim_num) %>%
  summarize_at(vars(subj_beta0_delinked, subj_beta1_delinked, subj_pMem_effect), list(max = max, min = min)) 

```

##### Across-sim max pre condition circSD

```{r fig.width=10, fig.height=6}

plot_grid(

  #What is the max subject pre condition value in each dataset
  sim_subj_extremes %>%
  ggplot() + 
  geom_histogram(aes(x = subj_beta0_delinked_max, fill = "red", alpha = 0.3), binwidth = 0.02) +
  theme(legend.position = "none") + 
  labs(x = "pre condition: max subj pMem per sim [subj_beta0_delinked_max]",
       subtitle = glue("p(< 0.05) = {sum(sim_subj_extremes$subj_beta0_delinked_max < 0.05)/length(sim_subj_extremes$subj_beta0_delinked_max)}\n p(> 0.95) = {sum(sim_subj_extremes$subj_beta0_delinked_max > 0.95)/length(sim_subj_extremes$subj_beta0_delinked_max)}"))
  
  ,

  #What is the max subject post condition value in each dataset
  sim_subj_extremes %>%
  ggplot() + 
  geom_histogram(aes(x = subj_beta1_delinked_max, fill = "red", alpha = 0.3), binwidth = 0.02) + 
  theme(legend.position = "none") + 
  labs(x = "post condition: max subj pMem per sim [subj_beta1_delinked_max]",
       subtitle = glue("p(< 0.05) = {sum(sim_subj_extremes$subj_beta1_delinked_max < 0.05)/length(sim_subj_extremes$subj_beta1_delinked_max)}\n p(>0.95) = {sum(sim_subj_extremes$subj_beta1_delinked_max > 0.95)/length(sim_subj_extremes$subj_beta1_delinked_max)}"))

  ,
  ncol =1,
  align = 'v'

)

```