---
title: "loo"
output: 
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    code_folding: "hide"
    theme: spacelab
params:
  model_dir_str: "/Users/zaworaca/Desktop/Desktop/zane/color_twoCond_diff/m4_[color_stm_STIM]"
  common_dir_str: "/Users/zaworaca/Desktop/Desktop/zane/color_twoCond_diff/common"
  save_dir_str: "/Users/zaworaca/Desktop/Desktop/zane/color_twoCond_diff/m4_[color_stm_STIM]/loo"
  loo_notes_str: ""    
    
---

<style type="text/css">

body{
  font-family: Helvetica;
}

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## libraries

```{r}

library(tidyverse)
library(brms)
library(bayesplot)
library(here)
library(glue)
library(scales)

theme_set(theme_light())

source(glue("{params$common_dir_str}/brms_model.R"))
source(glue("{params$model_dir_str}/model_prior.R"))

```

## data

```{r}

obs_only <- 
  read_csv(glue("{params$model_dir_str}/data/stimulation_obvs.csv")) %>%
  mutate(subj = as_factor(subj),
         obs_degree = error,
         error = obs_degree * (pi/180))

```

## full model

```{r}
print(bprior_full)
```


```{r}

iter = 4000
warmup = 2000
cores = 4
chains = 4
n_post_samples = (iter - warmup) * chains

fit_full <- brm(bform_full, obs_only, prior = bprior_full, 
                family = vm_uniform_mix, stanvars = stanvars,
                warmup = warmup, iter = iter, cores = cores, chains = chains, 
                control = list(adapt_delta = 0.99), inits = 0, 
                file =  glue("{params$save_dir_str}/fit_full"))

```

### fit check
#### divergences
```{r fig.width=6}

model_fit <- fit_full

#check neff and rhat and divergences
np <- nuts_params(model_fit)
rhat <- brms::rhat(model_fit)
neff_rat <- neff_ratio(model_fit)

np %>% 
  filter(Parameter == "divergent__") %>%
  summarise(n_div = sum(Value))
```

#### rhat
```{r fig.width=6}
mcmc_rhat(rhat) + yaxis_text(hjust = 1) + scale_x_continuous(breaks = pretty_breaks(6))
```

#### neff ratio
```{r fig.width=6}
mcmc_neff(neff_rat) + yaxis_text(hjust = 1)
```

#### trace plots
```{r fig.width=10, fig.height=6}
mcmc_trace(as.array(model_fit$fit))
```


## reduced model: no pre to post change on circSD parameter

```{r}
print(bprior_DcircSD_null)
```

```{r}

fit_DcircSD_null <- brm(bform_DcircSD_null, obs_only, prior = bprior_DcircSD_null, 
                        family = vm_uniform_mix, stanvars = stanvars,
                        warmup = warmup, iter = iter, cores = cores, chains = chains, 
                        control = list(adapt_delta = 0.99), inits = 0, 
                        file =  glue("{params$save_dir_str}/fit_DcircSD_null"))

```


### fit check
#### divergences
```{r fig.width=6}

model_fit <- fit_DcircSD_null

#check neff and rhat and divergences
np <- nuts_params(model_fit)
rhat <- brms::rhat(model_fit)
neff_rat <- neff_ratio(model_fit)

np %>% 
  filter(Parameter == "divergent__") %>%
  summarise(n_div = sum(Value))
```

#### rhat
```{r fig.width=6}
mcmc_rhat(rhat) + yaxis_text(hjust = 1) + scale_x_continuous(breaks = pretty_breaks(6))
```

#### neff ratio
```{r fig.width=6}
mcmc_neff(neff_rat) + yaxis_text(hjust = 1)
```

#### trace plots
```{r fig.width=10, fig.height=6}
mcmc_trace(as.array(model_fit$fit))
```


## reduced model: no pre to post change on pMem parameter

```{r}
print(bprior_DpMem_null)
```

```{r}

fit_DpMem_null <- brm(bform_DpMem_null, obs_only, prior = bprior_DpMem_null, 
                      family = vm_uniform_mix, stanvars = stanvars,
                      warmup = warmup, iter = iter, cores = cores, chains = chains, 
                      control = list(adapt_delta = 0.99), inits = 0, 
                      file = glue("{params$save_dir_str}/fit_DpMem_null"))

```

### fit check
#### divergences
```{r fig.width=6}

model_fit <- fit_DpMem_null

#check neff and rhat and divergences
np <- nuts_params(model_fit)
rhat <- brms::rhat(model_fit)
neff_rat <- neff_ratio(model_fit)

np %>% 
  filter(Parameter == "divergent__") %>%
  summarise(n_div = sum(Value))
```

#### rhat
```{r fig.width=6}
mcmc_rhat(rhat) + yaxis_text(hjust = 1) + scale_x_continuous(breaks = pretty_breaks(6))
```

#### neff ratio
```{r fig.width=6}
mcmc_neff(neff_rat) + yaxis_text(hjust = 1)
```

#### trace plots
```{r fig.width=10, fig.height=6}
mcmc_trace(as.array(model_fit$fit))
```


## reduced model: no pre to post change on pMem or circSD parameter

```{r}
bprior_DcircSD_DpMem_null
```

```{r}

fit_DcircSD_DpMem_null <- 
              brm(bform_DcircSD_DpMem_null, obs_only, prior = bprior_DcircSD_DpMem_null, 
                  family = vm_uniform_mix, stanvars = stanvars,
                  warmup = warmup, iter = iter, cores = cores, chains = chains, 
                  control = list(adapt_delta = 0.99), inits = 0, 
                  file = glue("{params$save_dir_str}/fit_DcircSD_DpMem_null"))

```

### fit check
#### divergences
```{r fig.width=6}

model_fit <- fit_DcircSD_DpMem_null

#check neff and rhat and divergences
np <- nuts_params(model_fit)
rhat <- brms::rhat(model_fit)
neff_rat <- neff_ratio(model_fit)

np %>% 
  filter(Parameter == "divergent__") %>%
  summarise(n_div = sum(Value))
```

#### rhat
```{r fig.width=6}
mcmc_rhat(rhat) + yaxis_text(hjust = 1) + scale_x_continuous(breaks = pretty_breaks(6))
```

#### neff ratio
```{r fig.width=6}
mcmc_neff(neff_rat) + yaxis_text(hjust = 1)
```

#### trace plots
```{r fig.width=10, fig.height=6}
mcmc_trace(as.array(model_fit$fit))
```

## loo compare


```{r}

#need to do this only once?
expose_functions(fit_full, vectorize = TRUE)

fit_full <- add_waic(fit_full, file = glue("{params$save_dir_str}/fit_full"))
fit_DcircSD_null <- add_waic(fit_DcircSD_null, file = glue("{params$save_dir_str}/fit_DcircSD_null"))
fit_DpMem_null <- add_waic(fit_DpMem_null, file = glue("{params$save_dir_str}/fit_DpMem_null"))
fit_DcircSD_DpMem_null <- add_waic(fit_DcircSD_DpMem_null, file = glue("{params$save_dir_str}/fit_DcircSD_DpMem_null"))

print("fit_full")
fit_full$waic

print("fit_DcircSD_null")
fit_DcircSD_null$waic

print("fit_DpMem_null")
fit_DpMem_null$waic

print("fit_DcircSD_DpMem_null")
fit_DcircSD_DpMem_null$waic

loo_compare(fit_full, fit_DcircSD_null, fit_DpMem_null, fit_DcircSD_DpMem_null, criterion = "waic")

```

## *Notes

```{r echo=FALSE, results="asis"}

# display solution as math
cat(paste0(params$loo_notes_str), sep="\n")

```