---
title: "model_fitting"
output: 
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    code_folding: "hide"
    theme: spacelab
fig_width: 10 
fig_height: 6
params:
  model_dir_str: "/Users/zaworaca/Desktop/Desktop/zane/color_twoCond_diff/m1_[color_stm_STIM]"
  common_dir_str: "/Users/zaworaca/Desktop/Desktop/zane/color_twoCond_diff/common"
  save_dir_str: "/Users/zaworaca/Desktop/Desktop/zane/color_twoCond_diff/m1_[color_stm_STIM]/model_fitting_actual"
  posterior_notes_str: ""
  fit_qc_notes_str: ""
  posterior_pred_notes_str: ""
---

<style type="text/css">

body{
  font-family: Helvetica;
}

</style>

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width = 6)
knitr::opts_chunk$set(fig.width = 10)


library(tidyverse)
library(brms)
library(tidybayes)
library(bayesplot)
library(cowplot)
library(scales)
library(hexbin)
library(glue)
library(matrixStats)

theme_set(theme_light())

source(glue("{params$common_dir_str}/brms_model.R"))
source(glue("{params$common_dir_str}/simulation.R"))

```


## load obs

```{r}

obs_only <- 
  read_csv(glue("{params$model_dir_str}/data/stimulation_obvs.csv")) %>%
  mutate(subj = as_factor(subj),
         obs_degree = error,
         error = obs_degree * (pi/180))

# obs_only <- sim_data %>%
#   unnest(subj_obs) %>%
#   select(subj_index = subj, 
#          error = obs_radian,
#          obs_degree, 
#          stimulation)



```

## peek at data

##### pre

```{r}
obs_only %>% 
  filter(stimulation == 0) %>%
  ggplot(aes(x = obs_degree)) +
  geom_histogram(binwidth = 10, aes(y=..density..)) + 
  geom_rug() + 
  geom_density(aes(y=..density..)) +  
  facet_wrap(vars(subj), ncol = 1)
```

##### post

```{r}
obs_only %>% 
  filter(stimulation == 1) %>%
  ggplot(aes(x = obs_degree)) +
  geom_histogram(binwidth = 10, aes(y=..density..)) + 
  geom_rug() + 
  geom_density(aes(y=..density..)) +  
  facet_wrap(vars(subj), ncol = 1)
```

## fit brms

```{r}

source(glue("{params$model_dir_str}/model_prior.R"))

print(bprior_full)

iter = 4000
warmup = 2000
cores = 4
chains = 4
n_post_samples = (iter - warmup) * chains

writeLines(
  make_stancode(bform_full, obs_only, family = vm_uniform_mix, prior = bprior_full, stanvars = stanvars),
  glue("{params$save_dir_str}/stan_code.txt")
)

model_fit <- brm(bform_full, obs_only, family = vm_uniform_mix, prior = bprior_full, stanvars = stanvars,
                 sample_prior = "yes",
                 warmup = warmup, iter = iter, cores = cores, chains = chains, 
                 control = list(adapt_delta = 0.99), inits = 0, 
                 file = glue("{params$save_dir_str}/obs_model_fit"))

print(model_fit)

```

## fit check
### divergences
```{r fig.width=6}

#check neff and rhat and divergences
np <- nuts_params(model_fit)
rhat <- brms::rhat(model_fit)
neff_rat <- neff_ratio(model_fit)

np %>% 
  filter(Parameter == "divergent__") %>%
  summarise(n_div = sum(Value))
```


### rhat
```{r fig.width=6}
mcmc_rhat(rhat) + yaxis_text(hjust = 1) + scale_x_continuous(breaks = pretty_breaks(6))
```


### neff ratio
```{r fig.width=6}
mcmc_neff(neff_rat) + yaxis_text(hjust = 1)
```

### trace plots
```{r fig.width=10, fig.height=6}
mcmc_trace(as.array(model_fit$fit))
```

### other
```{r fig.width=10, fig.height=6}
plot(model_fit, ask = FALSE)
```

### * Notes

```{r echo=FALSE, results="asis"}

# display solution as math
cat(paste0(params$fit_qc_notes_str), sep="\n")

```

## plot posteriors

### arrange samples

```{r}

# compute summaries for plot

group_level_samples <- 
  spread_draws(model_fit, `(b|sd)_.*`, regex = TRUE) %>%
  mutate(
         # group level parameters
         circSD_pre_mean  = exp(b_circSD_intercept),
         circSD_post_mean = exp(b_circSD_intercept + b_circSD_stimulation),
         circSD_ES_mean   = circSD_post_mean - circSD_pre_mean,
         pMem_pre_mean    = inv_logit(b_theta_intercept),
         pMem_post_mean   = inv_logit(b_theta_intercept + b_theta_stimulation),
         pMem_ES_mean     = pMem_post_mean - pMem_pre_mean,
         # predicitve dist for group level parameters
         circSD_pre_pred  = exp(rnorm(n(), b_circSD_intercept, sd_subj__circSD_Intercept)),
         circSD_post_pred = exp(rnorm(n(), b_circSD_intercept, sd_subj__circSD_Intercept) + 
                                rnorm(n(), b_circSD_stimulation, sd_subj__circSD_stimulation)),
         circSD_ES_pred   = circSD_post_pred - circSD_pre_pred,
         pMem_pre_pred    = inv_logit(rnorm(n(), b_theta_intercept, sd_subj__theta_Intercept)),
         pMem_post_pred   = inv_logit(rnorm(n(), b_theta_intercept, sd_subj__theta_Intercept) +
                                    rnorm(n(), b_theta_stimulation, sd_subj__theta_stimulation)),
         pMem_ES_pred     = pMem_post_pred - pMem_pre_pred
         ) %>% 
  select(-contains("b_"), -contains("sd_subj")) %>%
  pivot_longer(-contains("."), names_to = c("param", "stat"), names_pattern = "(.*)_(.*)", values_to = "value") %>%
  pivot_wider(names_from = stat, values_from = value)
  
group_level_summary <- 
  group_level_samples %>%
  group_by(param) %>%
  median_qi(.width = c(.5, .8, .95))



circSD_subj_samples <- 
  model_fit %>%
  spread_draws(b_circSD_intercept, b_circSD_stimulation, r_subj__circSD[subj, term]) %>%
  ungroup() %>%
  pivot_wider(names_from = term, values_from = r_subj__circSD, names_prefix = "offset_") %>%
  mutate(subj = subj,
        circSD_pre = exp(b_circSD_intercept + offset_Intercept),
        circSD_post = exp(b_circSD_intercept + offset_Intercept + b_circSD_stimulation + offset_stimulation),
        circSD_ES = circSD_post - circSD_pre) %>%
  select(-c(b_circSD_intercept, offset_Intercept, b_circSD_stimulation, offset_stimulation)) %>%
  pivot_longer(contains("circSD"), names_to = "param", values_to = "value") 

circSD_subj_summary <- 
  circSD_subj_samples %>%
  group_by(subj, param) %>%
  median_qi(.width = c(.90, .95))
  


pMem_subj_samples <- 
  model_fit %>%
  spread_draws(b_theta_intercept, b_theta_stimulation, r_subj__theta[subj, term]) %>%
  ungroup() %>%
  pivot_wider(names_from = term, values_from = r_subj__theta, names_prefix = "offset_") %>%
  mutate(subj = subj,
            pMem_pre = inv_logit(b_theta_intercept + offset_Intercept),
            pMem_post = inv_logit(b_theta_intercept + offset_Intercept + b_theta_stimulation + offset_stimulation),
            pMem_ES = pMem_post - pMem_pre) %>%
  select(-c(b_theta_intercept, offset_Intercept, b_theta_stimulation, offset_stimulation)) %>%
  pivot_longer(contains("pMem"), names_to = "param", values_to = "value") 

pMem_subj_summary <- 
  pMem_subj_samples %>%
  group_by(subj, param) %>%
  median_qi(.width = c(.90, .95))
    
``` 

```{r}
group_level_samples %>%
  select(-pred) %>%
  group_by(param) %>%
  median_qi(.width = c(.95))
```

### group level posteriors

```{r fig.width=8, fig.height=8}

circSD_p1 <- group_level_samples %>% 
  filter(str_detect(param, "circSD")) %>%
  ggplot() + 
  # posterior dist + interval for group mean
  geom_halfeyeh(aes(y = param, x = mean), .width = c(.90, .95), position = position_nudge(y = 0.15)) + 
  # posterior predictive distribution for group means
  stat_intervalh(aes(y = param, x = pred), .width = c(.5, .8, .95)) +
  # posterior medians for each parameter estimate per subj
  geom_point(data = circSD_subj_summary, aes(y = param, x = value), size = 2) +
  # decorations
  scale_color_brewer() + 
  scale_x_continuous(breaks = pretty_breaks(10)) + 
  coord_cartesian(xlim=c(-50, 150)) +
  labs(subtitle = "circSD: group level mean posterior (median, 90%, 95% interval), \nsubject posterior medians, \ncondition predictive dist of subjects", 
       x = "circSD", 
       color = "interval")

# group level pMem pre, post and ES plot

pMem_p1 <- group_level_samples %>% 
  filter(str_detect(param, "pMem")) %>%
  ggplot() + 
  # posterior dist + interval for group mean
  geom_halfeyeh(aes(y = param, x = mean), .width = c(.90, .95), position = position_nudge(y = 0.15)) + 
  # posterior predictive distribution for group means
  stat_intervalh(aes(y = param, x = pred), .width = c(.5, .8, .95)) +
  # posterior medians for each parameter estimate per subj
  geom_point(data = pMem_subj_summary, aes(y = param, x = value), size = 2) +
  # decorations
  scale_color_brewer() + 
  scale_x_continuous(breaks = pretty_breaks(10)) + 
  #coord_cartesian(xlim=c(-50, 150)) +
  labs(subtitle = "pMem: group level mean posterior (median, 90%, 95% interval), \nsubject posterior medians, \ncondition predictive dist of subjects", 
       x = "pMem", 
       color = "interval")

plot_grid(circSD_p1, pMem_p1, align = "hv", ncol = 1)

```


### circSD pre, post, ES

```{r, fig.width=9, fig.height=13}
  
# circSD pre: group level posteriors and subject posteriors

circSD_p2 <- 
  ggplot() + 
  # plot group mean circSD_pre posterior and subject circSD_pre posterior
  geom_halfeyeh(data = rbind(
                              group_level_samples %>% 
                              filter(str_detect(param, "circSD_pre")) %>%
                              select(-pred, value = mean)
                            ,
                              circSD_subj_samples %>%
                              filter(str_detect(param, "circSD_pre")) %>%
                              unite(param, param, subj) )
                , aes(y = param, x = value), .width = c(.90, .95)) + 
  # plot pre condition group predictive distribution
  stat_intervalh(data = group_level_samples %>% filter(str_detect(param, "circSD_pre")),
                 aes(y = param , x = pred),
                 .width = c(.5, .8, .95),
                 position = position_nudge(y = -0.15)
                   ) +
  # show modeled subject circSD_pre posterior medians in the prediction band
  geom_point(data = circSD_subj_summary %>% filter(param == "circSD_pre"),
             aes(y = param, x = value), 
             size = 2, 
             position = position_nudge(y = -0.15)) + 
  scale_color_brewer() + 
  scale_x_continuous(breaks = pretty_breaks(10)) + 
  labs(subtitle = "circSD_pre: group level mean posterior (median, 90%, 95% interval), \nsubject posterior, \ncondition predictive dist of subjects",
       x = "circSD",
       color = "interval")



circSD_p3 <-   
  ggplot() + 
  # plot group mean circSD_post posterior and subject circSD_post posterior
  geom_halfeyeh(data = rbind(
                              group_level_samples %>% 
                              filter(str_detect(param, "circSD_post")) %>%
                              select(-pred, value = mean)
                            ,
                              circSD_subj_samples %>%
                              filter(str_detect(param, "circSD_post")) %>%
                              unite(param, param, subj) )
                , aes(y = param, x = value), .width = c(.90, .95)) + 
  # plot post condition group predictive distribution
  stat_intervalh(data = group_level_samples %>% filter(str_detect(param, "circSD_post")),
                 aes(y = param , x = pred),
                 .width = c(.5, .8, .95),
                 position = position_nudge(y = -0.15)
                   ) +
  # show modeled subject circSD_post posterior medians in the prediction band
  geom_point(data = circSD_subj_summary %>% filter(param == "circSD_post"),
             aes(y = param, x = value), 
             size = 2, 
             position = position_nudge(y =  -0.15)) + 
  scale_color_brewer() + 
  scale_x_continuous(breaks = pretty_breaks(10)) + 
  labs(subtitle = "circSD_post: group level mean posterior (median, 90%, 95% interval), \nsubject posterior, \ncondition predictive dist of subjects",
       x = "circSD",
       color = "interval")


circSD_p4 <- 
  ggplot() + 
  # plot group mean circSD_ES posterior and subject circSD_ES posterior
  geom_halfeyeh(data = rbind(
                              group_level_samples %>% 
                              filter(str_detect(param, "circSD_ES")) %>%
                              select(-pred, value = mean)
                            ,
                              circSD_subj_samples %>%
                              filter(str_detect(param, "circSD_ES")) %>%
                              unite(param, param, subj) )
                , aes(y = param, x = value), .width = c(.90, .95)) + 
  # plot ES  group predictive distribution
  stat_intervalh(data = group_level_samples %>% filter(str_detect(param, "circSD_ES")),
                 aes(y = param , x = pred),
                 .width = c(.5, .8, .95),
                 position = position_nudge(y = -0.15)
                   ) +
  # show modeled subject circSD_ES posterior medians in the prediction band
  geom_point(data = circSD_subj_summary %>% filter(param == "circSD_ES"),
             aes(y = param, x = value), 
             size = 2, 
             position = position_nudge(y =  -0.15)) + 
  scale_color_brewer() + 
  scale_x_continuous(breaks = pretty_breaks(10)) + 
  labs(subtitle = "circSD_ES: group level mean posterior (median, 90%, 95% interval), \nsubject posterior, \nES predictive dist of subjects",
       x = "detla circSD",
       color = "interval")


plot_grid(circSD_p2, circSD_p3, circSD_p4, ncol = 1, align = "hv")

```


### pMem pre, post, ES

```{r, fig.width=9, fig.height=13}

  
# pMem_ pre: group level posteriors and subject posteriors

pMem_p2 <- 
  ggplot() + 
  # plot group mean pMem__pre posterior and subject cpMem__pre posterior
  geom_halfeyeh(data = rbind(
                              group_level_samples %>% 
                              filter(str_detect(param, "pMem_pre")) %>%
                              select(-pred, value = mean)
                            ,
                              pMem_subj_samples %>%
                              filter(str_detect(param, "pMem_pre")) %>%
                              unite(param, param, subj) )
                , aes(y = param, x = value), .width = c(.90, .95)) + 
  # plot pre condition group predictive distribution
  stat_intervalh(data = group_level_samples %>% filter(str_detect(param, "pMem_pre")),
                 aes(y = param , x = pred),
                 .width = c(.5, .8, .95),
                 position = position_nudge(y = -0.15)
                   ) +
  # show modeled subject pMem_pre posterior medians in the prediction band
  geom_point(data = pMem_subj_summary %>% filter(param == "pMem_pre"),
             aes(y = param, x = value), 
             size = 2, 
             position = position_nudge(y = -0.15)) + 
  scale_color_brewer() + 
  scale_x_continuous(breaks = pretty_breaks(10)) + 
  labs(subtitle = "pMem_pre: group level mean posterior (median, 90%, 95% interval), \nsubject posterior, \ncondition predictive dist of subjects",
       x = "pMem",
       color = "interval")



pMem_p3 <-   
  ggplot() + 
  # plot group mean pMem_post posterior and subject pMem_post posterior
  geom_halfeyeh(data = rbind(
                              group_level_samples %>% 
                              filter(str_detect(param, "pMem_post")) %>%
                              select(-pred, value = mean)
                            ,
                              pMem_subj_samples %>%
                              filter(str_detect(param, "pMem_post")) %>%
                              unite(param, param, subj) )
                , aes(y = param, x = value), .width = c(.90, .95)) + 
  # plot post condition group predictive distribution
  stat_intervalh(data = group_level_samples %>% filter(str_detect(param, "pMem_post")),
                 aes(y = param , x = pred),
                 .width = c(.5, .8, .95),
                 position = position_nudge(y = -0.15)
                   ) +
  # show modeled subject pMem_post posterior medians in the prediction band
  geom_point(data = pMem_subj_summary %>% filter(param == "pMem_post"),
             aes(y = param, x = value), 
             size = 2, 
             position = position_nudge(y =  -0.15)) + 
  scale_color_brewer() + 
  scale_x_continuous(breaks = pretty_breaks(10)) + 
  labs(subtitle = "pMem_post: group level mean posterior (median, 90%, 95% interval), \nsubject posterior, \ncondition predictive dist of subjects",
       x = "pMem",
       color = "interval")


pMem_p4 <- 
  ggplot() + 
  # plot group mean pMem_ES posterior and subject pMem_ES posterior
  geom_halfeyeh(data = rbind(
                              group_level_samples %>% 
                              filter(str_detect(param, "pMem_ES")) %>%
                              select(-pred, value = mean)
                            ,
                              pMem_subj_samples %>%
                              filter(str_detect(param, "pMem_ES")) %>%
                              unite(param, param, subj) )
                , aes(y = param, x = value), .width = c(.90, .95)) + 
  # plot ES  group predictive distribution
  stat_intervalh(data = group_level_samples %>% filter(str_detect(param, "pMem_ES")),
                 aes(y = param , x = pred),
                 .width = c(.5, .8, .95),
                 position = position_nudge(y = -0.15)
                   ) +
  # show modeled subject pMem_ES posterior medians in the prediction band
  geom_point(data = pMem_subj_summary %>% filter(param == "pMem_ES"),
             aes(y = param, x = value), 
             size = 2, 
             position = position_nudge(y =  -0.15)) + 
  scale_color_brewer() + 
  scale_x_continuous(breaks = pretty_breaks(10)) + 
  labs(subtitle = "pMem_ES: group level mean posterior (median, 90%, 95% interval), \nsubject posterior, \nES predictive dist of subjects",
       x = "detla pMem",
       color = "interval")

```

```{r fig.width=9, fig.height=13}
plot_grid(pMem_p2, pMem_p3, pMem_p4, ncol = 1, align = "hv")
```


### group level joint posteriors

```{r fig.width=8, fig.height=8}

group_level_samples %>%
  pivot_wider(id_cols = contains("."), names_from = param, values_from = mean) %>%
  select(-contains(".")) %>%
  mcmc_pairs(off_diag_fun = "hex")

```

## plot posteriors w/ priors

```{r}

# compute summaries for plot with priors

group_level_samples <- 
  spread_draws(model_fit, `(prior_)?(b|sd)_.*`, regex = TRUE) %>%
  mutate(
         # prior
         # group level parameters
         prior_circSD_pre_mean  = exp(prior_b_circSD_intercept),
         prior_circSD_post_mean = exp(prior_b_circSD_intercept + prior_b_circSD_stimulation),
         prior_circSD_ES_mean   = prior_circSD_post_mean - prior_circSD_pre_mean,
         prior_pMem_pre_mean    = inv_logit(prior_b_theta_intercept),
         prior_pMem_post_mean   = inv_logit(prior_b_theta_intercept + prior_b_theta_stimulation),
         prior_pMem_ES_mean     = prior_pMem_post_mean - prior_pMem_pre_mean,   
         # predicitve dist for group level parameters
         prior_circSD_pre_pred  = exp(rnorm(n(), prior_b_circSD_intercept, prior_sd_subj__circSD_Intercept)),
         prior_circSD_post_pred = exp(rnorm(n(), prior_b_circSD_intercept, prior_sd_subj__circSD_Intercept) + 
                                rnorm(n(), prior_b_circSD_stimulation, prior_sd_subj__circSD_stimulation)),
         prior_circSD_ES_pred   = prior_circSD_post_pred - prior_circSD_pre_pred,
         prior_pMem_pre_pred    = inv_logit(rnorm(n(), prior_b_theta_intercept, prior_sd_subj__theta_Intercept)),
         prior_pMem_post_pred   = inv_logit(rnorm(n(), prior_b_theta_intercept, prior_sd_subj__theta_Intercept) +
                                    rnorm(n(), prior_b_theta_stimulation, prior_sd_subj__theta_stimulation)),
         prior_pMem_ES_pred     = prior_pMem_post_pred - prior_pMem_pre_pred,
         
         # posteriors
         # group level parameters
         circSD_pre_mean  = exp(b_circSD_intercept),
         circSD_post_mean = exp(b_circSD_intercept + b_circSD_stimulation),
         circSD_ES_mean   = circSD_post_mean - circSD_pre_mean,
         pMem_pre_mean    = inv_logit(b_theta_intercept),
         pMem_post_mean   = inv_logit(b_theta_intercept + b_theta_stimulation),
         pMem_ES_mean     = pMem_post_mean - pMem_pre_mean,
         # predicitve dist for group level parameters
         circSD_pre_pred  = exp(rnorm(n(), b_circSD_intercept, sd_subj__circSD_Intercept)),
         circSD_post_pred = exp(rnorm(n(), b_circSD_intercept, sd_subj__circSD_Intercept) + 
                                rnorm(n(), b_circSD_stimulation, sd_subj__circSD_stimulation)),
         circSD_ES_pred   = circSD_post_pred - circSD_pre_pred,
         pMem_pre_pred    = inv_logit(rnorm(n(), b_theta_intercept, sd_subj__theta_Intercept)),
         pMem_post_pred   = inv_logit(rnorm(n(), b_theta_intercept, sd_subj__theta_Intercept) +
                                    rnorm(n(), b_theta_stimulation, sd_subj__theta_stimulation)),
         pMem_ES_pred     = pMem_post_pred - pMem_pre_pred
         ) %>% 
  select(-contains("b_"), -contains("sd_subj")) %>%
  pivot_longer(-contains("."), names_to = c( "param", "stat"), names_pattern = "(.*)_(.*)", values_to = "value") %>%
  pivot_wider(names_from = stat, values_from = value)


```

### group level posteriors

```{r fig.width=8, fig.height=13}


circSD_p1_wPrior <- 
  group_level_samples %>% 
  filter(str_detect(param, "circSD")) %>% 
  mutate(param = fct_relevel(param, c("prior_circSD_ES", "circSD_ES", "prior_circSD_pre", "circSD_pre", "prior_circSD_post", "circSD_post"))) %>%
  ggplot() + 
  
  # posterior dist + interval for group mean
  geom_halfeyeh(aes(y = param, x = mean), .width = c(.90, .95), position = position_nudge(y = 0.15)) + 
  # posterior predictive distribution for group means
  stat_intervalh(aes(y = param, x = pred), .width = c(.5, .8, .95)) +
  # posterior medians for each parameter estimate per subj
  geom_point(data = circSD_subj_summary, aes(y = param, x = value), size = 2) +
  
  # prior dist + interval for group mean
  #geom_halfeyeh(data = group_level_prior_param_samples, aes(y = param, x = values), .width = c(.90, .95)) +
  
  # decorations
  scale_color_brewer() + 
  scale_x_continuous(breaks = pretty_breaks(10)) + 
  coord_cartesian(xlim=c(-50, 150)) +
  labs(subtitle = "circSD: group level mean prior + posterior (median, 90%, 95% interval), \nsubject posterior medians, \ncondition predictive dist of subjects", 
       x = "circSD", 
       color = "interval")



# group level pMem pre, post and ES plot

pMem_p1_wPrior <- 
  group_level_samples %>% 
  filter(str_detect(param, "pMem")) %>%
  mutate(param = fct_relevel(param, c("prior_pMem_ES", "pMem_ES", "prior_pMem_pre", "pMem_pre", "prior_pMem_post", "pMem_post"))) %>%
  ggplot() + 
  
  # posterior dist + interval for group mean
  geom_halfeyeh(aes(y = param, x = mean), .width = c(.90, .95), position = position_nudge(y = 0.15)) + 
  # posterior predictive distribution for group means
  stat_intervalh(aes(y = param, x = pred), .width = c(.5, .8, .95)) +
  # posterior medians for each parameter estimate per subj
  geom_point(data = pMem_subj_summary, aes(y = param, x = value), size = 2) +
  
  # decorations
  scale_color_brewer() + 
  scale_x_continuous(breaks = pretty_breaks(10)) + 
  #coord_cartesian(xlim=c(-50, 150)) +
  labs(subtitle = "pMem: group level mean prior + posterior (median, 90%, 95% interval), \nsubject posterior medians, \ncondition predictive dist of subjects", 
       x = "pMem", 
       color = "interval")

plot_grid(circSD_p1_wPrior, pMem_p1_wPrior, align = "hv", ncol = 1)

```

### * Notes

```{r echo=FALSE, results="asis"}

# display solution as math
cat(paste0(params$posterior_notes_str), sep="\n")

```


## posterior predictive plot of errors


### sim

```{r results="hide"}

conditions <- c(0,1)
nobs_per_cond_sim <- 1500

post_pred_fpath <- glue("{params$save_dir_str}/post_pred_obs.rds")

if (file.exists(post_pred_fpath)){
  
  post_pred_sim <- readRDS(post_pred_fpath)

}else{

  print("simulating")
  
  posterior_arranged <- 
    spread_draws(model_fit, `(b|sd)_.*`, regex = TRUE) %>%
    sample_n(2e3) %>%
    mutate(sim_num = 1:n(),
           nsubj = 1,
           nobs_per_cond = nobs_per_cond_sim) %>%
    select(-contains(".")) %>%
    select(sim_num,
           alpha0_mu = b_circSD_intercept,
           alpha0_sigma = sd_subj__circSD_Intercept,
           alphaD_mu = b_circSD_stimulation,
           alphaD_sigma = sd_subj__circSD_stimulation,
           beta0_mu = b_theta_intercept,
           beta0_sigma = sd_subj__theta_Intercept,
           betaD_mu = b_theta_stimulation,
           betaD_sigma = sd_subj__theta_stimulation,
           nsubj,
           nobs_per_cond) 
  
  post_pred_sim <- 
    posterior_arranged %>%
    mutate(
      # use draw_subj to sample nsubj_sim per sim using group-level parameter draws
      dataset = pmap(posterior_arranged, draw_subj),
      stimulation = list(stimulation = rep(conditions, each = nobs_per_cond_sim))) %>%
    
    # first unnest dataset, expanding by nsubj_sim and copying stimulation list to each subj
    unnest(dataset) %>%
    
    # then unnest stimulation, expanding by nobs_per_cond_sim*2
    unnest(stimulation) %>%
    
    # now use likelihood to simulation observations
    mutate(
      # evaluate and delink linear model on pMem
      pMem = inv_logit(subj_beta0 + (subj_betaD * stimulation)),
      
      # evaluate and delink linear model on circSD/kappa
      k = sd2k_vec(
        pracma::deg2rad(
          exp(subj_alpha0 + (subj_alphaD * stimulation)))),
      
      # use pMem to draw a 1 or 0 for each trial
      memFlip = rbernoulli(n(), pMem),
      
      # use k to draw from vonMises for each trial
      vm_draw = rvonmises_vec(1, pi, k) - pi,
      
      # draw from unif for each trial
      unif_draw = runif(n(), -pi, pi),
      
      # assign either vm_draw or unif_draw to each trial, depending on memFlip
      obs_radian = memFlip * vm_draw + (1 - memFlip) * unif_draw,
      
      # convert to degrees
      obs_degree = obs_radian * (180/pi)
    ) %>%
    select(-c(pMem, k, memFlip, vm_draw, unif_draw)) %>%
    nest(subj_obs = c(stimulation, obs_degree, obs_radian)) %>%
    nest(dataset = c(subj, subj_alpha0, subj_alphaD, subj_beta0, subj_betaD, nobs_per_condition, subj_obs))

  
  saveRDS(post_pred_sim, post_pred_fpath)
  
}

```

```{r results="hide"}

conditions <- c(0,1)
nobs_per_cond_sim <- 1500

post_predmean_fpath <- glue("{params$save_dir_str}/post_predmean_obs.rds")

if (file.exists(post_predmean_fpath)){
  
  post_predmean_sim <- readRDS(post_predmean_fpath)

}else{

  posterior_arranged <- 
    spread_draws(model_fit, `(b|sd)_.*`, regex = TRUE) %>%
    sample_n(2e3) %>%
    mutate(sim_num = 1:n(),
           nobs_per_cond = nobs_per_cond_sim ) %>%
    select(-contains(".")) %>%
    select(sim_num,
           subj_alpha0 = b_circSD_intercept,
           subj_alphaD = b_circSD_stimulation,
           subj_beta0 = b_theta_intercept,
           subj_betaD = b_theta_stimulation,
           nobs_per_cond) 

  post_predmean_sim <- 
    posterior_arranged %>%
    
    # add stimulation covariates
    mutate(
      stimulation = list(stimulation = rep(conditions, each = nobs_per_cond_sim))
    ) %>%
    
    # then unnest stimulation, expanding by nobs_per_cond_sim*2
    unnest(stimulation) %>%
    
    # now use likelihood to simulation observations
    mutate(
      
      # evaluate and delink linear model on pMem
      pMem = inv_logit(subj_beta0 + (subj_betaD * stimulation)),
      
      # evaluate and delink linear model on circSD/kappa
      k = sd2k_vec(
        pracma::deg2rad(
          exp(subj_alpha0 + (subj_alphaD * stimulation)))),
      
      # use pMem to draw a 1 or 0 for each trial
      memFlip = rbernoulli(n(), pMem),
      
      # use k to draw from vonMises for each trial
      vm_draw = rvonmises_vec(1, pi, k) - pi,
      
      # draw from unif for each trial
      unif_draw = runif(n(), -pi, pi),
      
      # assign either vm_draw or unif_draw to each trial, depending on memFlip
      obs_radian = memFlip * vm_draw + (1 - memFlip) * unif_draw,
      
      # convert to degrees
      obs_degree = obs_radian * (180/pi)
      
    ) %>%
    select(-c(pMem, k, memFlip, vm_draw, unif_draw)) %>%
    nest(dataset = c(stimulation, obs_degree, obs_radian)) 

  
  saveRDS(post_predmean_sim, post_predmean_fpath)
  
}

```

### posterior data prediction, w/ group-level variance


```{r fig.width=10, fig.height=6}

#######################################################
# calculate histogram quantile mats from each condition

sim_subj_obs_hist_count <- function(dataset, condition = 0){
  
  dataset_obs <- dataset %>% 
    sample_n(1) %>%
    unnest(subj_obs) %>%
    filter(stimulation == condition) %>%
    select(obs_degree)
  
  breaks <- seq(-180, 180, 5)
  
  bincount <- hist(dataset_obs$obs_degree, breaks = breaks, plot = FALSE)$counts
  
  bincount_names <- glue("c{breaks[-1]}")
  
  names(bincount) <- bincount_names
  bincount_df <- data.frame(as.list(bincount))

  return(bincount_df)
  
}

make_quantmat <- function(sim_datasets, condition = 0){

  bincounts <- sim_datasets %>% 
  select(dataset) %>% 
  mutate(subj_hist_counts = map(dataset, sim_subj_obs_hist_count, condition)) %>% 
  select(-dataset) %>% 
  unnest(subj_hist_counts) %>%
  as_tibble()


  xvals <- seq(-177.5, 177.5, 5)
  probs <- seq(0.1,0.9,0.1)

  quantmat <- as.data.frame(matrix(NA, nrow=ncol(bincounts), ncol=length(probs)))
  names(quantmat) <- paste0("p",probs)

  quantmat <- cbind(quantmat, xvals)

  for (iQuant in 1:length(probs)){
   quantmat[,paste0("p",probs[iQuant])] <- as.numeric(summarise_all(bincounts, ~quantile(., probs[iQuant])))
  }
    
  return(quantmat)
}

quantmat_cond0 <- make_quantmat(post_pred_sim, 0)
quantmat_cond1 <- make_quantmat(post_pred_sim, 1)


#######################################################
# calculate ecdf quantile mats from each condition

# unnest post_pred_sim, using only 1 subj/dataset
unnested <- 
  post_pred_sim %>%
  unnest(dataset) %>%
  group_by(sim_num) %>%
  sample_n(1) %>%
  ungroup() %>%
  unnest(subj_obs)

# calc quantiles mat for pre condition
ecdf_res_stim0 <- 
  unnested %>% 
  filter(stimulation == 0) %>%
  group_by(sim_num) %>% 
  group_map(~ecdf(.$obs_degree )(seq(-180, 180, 1)))

stim0_ecdf_quantiles <- bind_cols(
  tibble(x_val = seq(-180, 180, 1)), 
  as_tibble(colQuantiles(do.call(rbind, ecdf_res_stim0), probs = c(0.95, 0.5, 0.05 )))
  )

# calc quantiles mat for post condition
ecdf_res_stim1 <- 
  unnested %>% 
  filter(stimulation == 1) %>%
  group_by(sim_num) %>% 
  group_map(~ecdf(.$obs_degree )(seq(-180, 180, 1)))

stim1_ecdf_quantiles <- bind_cols(
  tibble(x_val = seq(-180, 180, 1)), 
  as_tibble(colQuantiles(do.call(rbind, ecdf_res_stim1), probs = c(0.95, 0.5, 0.05 )))
  )

                      
```

```{r fig.width=8, fig.height=6}

# blues
b_light <- "#8C9BC4"
b_light_highlight <- "#A0ADCE"
b_mid   <- "#546BA9"
b_mid_highlight   <- "#7385B8"
b_dark  <- "#002381"
b_dark_highlight  <- "#2E4B97"

#betancourt reds
r_light <- "#DCBCBC"
r_light_highlight <- "#C79999"
r_mid   <- "#B97C7C"
r_mid_highlight   <- "#A25050"
r_dark  <- "#8F2727"
r_dark_highlight  <- "#7C0000"


#######################################################
# plot histogram(density) per condition

ggplot(quantmat_cond0, aes(x = xvals)) + 
  geom_ribbon(aes(ymax = p0.9, ymin = p0.1), fill = r_light, alpha = 0.4) + 
  geom_line(aes(y = p0.5), color = r_dark, size = 1) + 
  geom_ribbon(data = quantmat_cond1, aes(ymax = p0.9, ymin = p0.1), fill = b_light, alpha = 0.4) + 
  geom_line(data = quantmat_cond1, aes(y = p0.5), color = b_dark, size = 1) + 
  scale_x_continuous(breaks=pretty_breaks(10)) + 
  labs(x = "error (degrees) [red = pre, blue = post]", 
       y = "count +/- quantile", 
       subtitle = glue("per-condition posterior pred dist (median line, 90% interval over {nrow(post_pred_sim)} sim datasets)\n({nobs_per_cond_sim} samples/cond, per subj-level draw, per group-level mean + sd draw)")) + 
  theme_cowplot()
```


```{r fig.width=10, fig.height=6}

#######################################################
# plot ecdf per condition

ggplot() +
  geom_ribbon(data = stim0_ecdf_quantiles, aes(x = x_val, ymax = `95%`, ymin = `5%`), fill = "red", alpha = 0.3) + 
  geom_line(data = stim0_ecdf_quantiles, aes(x = x_val, y = `50%`), color = "red", size = 1) +
  geom_ribbon(data = stim1_ecdf_quantiles, aes(x = x_val, ymax = `95%`, ymin = `5%`), fill = "blue", alpha = 0.3) + 
  geom_line(data = stim1_ecdf_quantiles, aes(x = x_val, y = `50%`), color = "blue", size = 1) + 
  scale_x_continuous(breaks=pretty_breaks(10)) + 
  geom_hline(yintercept = seq(0, 1, 0.25), linetype = "dashed", alpha = 0.2) +
  labs(x = "error (degrees) [red = pre, blue = post]", 
       y = "cumulative prob.", 
       subtitle = glue("per-condition posterior pred cdf (median line, 90% interval over {nrow(post_pred_sim)} sim datasets) \n({nobs_per_cond_sim} samples/cond, per subj-level draw, per group-level mean + sd draw")) + 
  theme_cowplot()



```

### posterior data prediction, w/o group-level variance

```{r}

#######################################################
# calculate histogram quantile mats from each condition

sim_single_subj_obs_hist_count <- function(dataset, condition = 0){
  
  dataset_obs <- dataset %>% 
    filter(stimulation == condition) %>%
    select(obs_degree)
  
  breaks <- seq(-180, 180, 5)
  
  bincount <- hist(dataset_obs$obs_degree, breaks = breaks, plot = FALSE)$counts
  
  bincount_names <- glue("c{breaks[-1]}")
  
  names(bincount) <- bincount_names
  bincount_df <- data.frame(as.list(bincount))

  return(bincount_df)
  
}

make_quantmat <- function(sim_datasets, condition = 0){

  bincounts <- sim_datasets %>% 
  select(dataset) %>% 
  mutate(subj_hist_counts = map(dataset, sim_single_subj_obs_hist_count, condition)) %>% 
  select(-dataset) %>% 
  unnest(subj_hist_counts) %>%
  as_tibble()


  xvals <- seq(-177.5, 177.5, 5)
  probs <- seq(0.1,0.9,0.1)

  quantmat <- as.data.frame(matrix(NA, nrow=ncol(bincounts), ncol=length(probs)))
  names(quantmat) <- paste0("p",probs)

  quantmat <- cbind(quantmat, xvals)

  for (iQuant in 1:length(probs)){
   quantmat[,paste0("p",probs[iQuant])] <- as.numeric(summarise_all(bincounts, ~quantile(., probs[iQuant])))
  }
    
  return(quantmat)
}

quantmat_cond0 <- make_quantmat(post_predmean_sim, 0)
quantmat_cond1 <- make_quantmat(post_predmean_sim, 1)


#######################################################
# calculate ecdf quantile mats from each condition

# unnest post_pred_sim, using only 1 subj/dataset
unnested <- 
  post_predmean_sim %>%
  unnest(dataset)

# calc quantiles mat for pre condition
ecdf_res_stim0 <- 
  unnested %>% 
  filter(stimulation == 0) %>%
  group_by(sim_num) %>% 
  group_map(~ecdf(.$obs_degree )(seq(-180, 180, 1)))

stim0_ecdf_quantiles <- bind_cols(
  tibble(x_val = seq(-180, 180, 1)), 
  as_tibble(colQuantiles(do.call(rbind, ecdf_res_stim0), probs = c(0.95, 0.5, 0.05 )))
  )

# calc quantiles mat for post condition
ecdf_res_stim1 <- 
  unnested %>% 
  filter(stimulation == 1) %>%
  group_by(sim_num) %>% 
  group_map(~ecdf(.$obs_degree )(seq(-180, 180, 1)))

stim1_ecdf_quantiles <- bind_cols(
  tibble(x_val = seq(-180, 180, 1)), 
  as_tibble(colQuantiles(do.call(rbind, ecdf_res_stim1), probs = c(0.95, 0.5, 0.05 )))
  )

                      
```

```{r fig.width=8, fig.height=6}

# blues
b_light <- "#8C9BC4"
b_light_highlight <- "#A0ADCE"
b_mid   <- "#546BA9"
b_mid_highlight   <- "#7385B8"
b_dark  <- "#002381"
b_dark_highlight  <- "#2E4B97"

#betancourt reds
r_light <- "#DCBCBC"
r_light_highlight <- "#C79999"
r_mid   <- "#B97C7C"
r_mid_highlight   <- "#A25050"
r_dark  <- "#8F2727"
r_dark_highlight  <- "#7C0000"


#######################################################
# plot histogram(density) per condition

ggplot(quantmat_cond0, aes(x = xvals)) + 
  geom_ribbon(aes(ymax = p0.9, ymin = p0.1), fill = r_light, alpha = 0.4) + 
  geom_line(aes(y = p0.5), color = r_dark, size = 1) + 
  geom_ribbon(data = quantmat_cond1, aes(ymax = p0.9, ymin = p0.1), fill = b_light, alpha = 0.4) + 
  geom_line(data = quantmat_cond1, aes(y = p0.5), color = b_dark, size = 1) + 
  scale_x_continuous(breaks=pretty_breaks(10)) + 
  labs(x = "error (degrees) [red = pre, blue = post]", 
       y = "count +/- quantile", 
       subtitle = glue("per-condition posterior pred dist (median line, 90% interval over {nrow(post_predmean_sim)} sim datasets)\n({nobs_per_cond_sim} samples/cond, per subj-level draw, per group-level mean draw)")) + 
  theme_cowplot()
```


```{r fig.width=10, fig.height=6}

#######################################################
# plot ecdf per condition

ggplot() +
  geom_ribbon(data = stim0_ecdf_quantiles, aes(x = x_val, ymax = `95%`, ymin = `5%`), fill = "red", alpha = 0.3) + 
  geom_line(data = stim0_ecdf_quantiles, aes(x = x_val, y = `50%`), color = "red", size = 1) +
  geom_ribbon(data = stim1_ecdf_quantiles, aes(x = x_val, ymax = `95%`, ymin = `5%`), fill = "blue", alpha = 0.3) + 
  geom_line(data = stim1_ecdf_quantiles, aes(x = x_val, y = `50%`), color = "blue", size = 1) + 
  scale_x_continuous(breaks=pretty_breaks(10)) + 
  geom_hline(yintercept = seq(0, 1, 0.25), linetype = "dashed", alpha = 0.2) +
  labs(x = "error (degrees) [red = pre, blue = post]", 
       y = "cumulative prob.", 
       subtitle = glue("per-condition posterior pred cdf (median line, 90% interval over {nrow(post_predmean_sim)} sim datasets) \n({nobs_per_cond_sim} samples/cond, per subj-level draw, per group-level mean draw")) + 
  theme_cowplot()



```

### * Notes

```{r echo=FALSE, results="asis"}

# display solution as math
cat(paste0(params$posterior_pred_notes_str), sep="\n")

```

