---
title: "explore_prior"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '/Users/zaworaca/Desktop/Desktop/zane/color_twoCond_diff/code')

```

```{r lib_load}

library(tidyverse)
library(Rfast) #VM sampler
library(pracma) #rad2deg conversions
library(glue)
library(cowplot)

theme_set(theme_cowplot())

```

```{r helper_func, echo=FALSE}


sd2k <- function(sd_input) {
  
  #sd_input needs to be radians

  #original matlab code
  # R <- exp(-S.^2/2);
  # K = 1./(R.^3 - 4 * R.^2 + 3 * R);
  # K(R < 0.85) = -0.4 + 1.39 * R(R < 0.85) + 0.43./(1 - R(R < 0.85));
  # K(R < 0.53) = 2 * R(R < 0.53) + R(R < 0.53).^3 + (5 * R(R < 0.53).^5)/6;

  R <- exp(-(sd_input^2)/2)
  K <- 1/((R^3) - (4 * R^2) + (3*R))
  
  if(R < 0.85){
    K <- -0.4 + (1.39 * R) + (0.43/(1-R))
  }
  
  if(R < 0.53){
    K <- (2 * R) + R^3 + (5 * R^5)/6
  }
  

  return(K)
}
sd2k_vec <- Vectorize(sd2k)




k2sd <- function(kappa_input){
  
  if (kappa_input == 0){
    sd <- Inf
  }else if (is.infinite(kappa_input)){
    sd <- 0
  }else{
    sd <- sqrt(-2*log(besselI(kappa_input, 1)/besselI(kappa_input, 0)))
  }
}
k2sd_vec <- Vectorize(k2sd)

```


Fitting a mixture model to a single subject, each radius is modelled seperately. The result is N*2 parameters, a p_guess and a kappa for each radius (per subject).


\begin{aligned}
error_i &\sim (1-p\_guess_i)*VM(0, \kappa_i) + (p\_guess_i)*Unif(0,2\pi) \\
\kappa_i &= sd2k(circ\_sd_i) \\
circ\_sd_i &= \alpha_{RADIUS[i]} \\
p\_guess_i &= \beta_{RADIUS[i]} \\

\alpha_{RADIUS} &\sim ?\\
\beta_{RADIUS} &\sim Beta(1, 1) ~~ (uniform ~ prior ~ on ~ each ~ \beta)

\end{aligned}


```{r prior_sim, fig.align='center', fig.height=10}

#function to simulate from von mises
sim_vm <- function(k){
  Rfast::rvonmises(1, pi, k, rads = TRUE)
}
sim_vm_vec <- Vectorize(sim_vm, vectorize.args = c("k"))

plot_prior_dist <- function(sd_deg_sim, title_str){
  
  # use prior sim and its implied data
  prior_sim <- tibble(sd_deg = sd_deg_sim) %>%
    mutate(sd_rad = deg2rad(sd_deg), kappa = sd2k_vec(sd_rad), sim_data = rad2deg(sim_vm_vec(kappa)) - 180)
  
  # calc some quantiles of prior on sd
  deg_sd_quantiles <- round(quantile(prior_sim$sd_deg, c(0.05, 0.95)),2)
  
  # plots
  deg_sd <- ggplot(prior_sim, aes(x = sd_deg)) + 
    geom_histogram(binwidth=1) + 
    labs(subtitle = glue("{title_str} prior on VM-circ_sd\n5%={deg_sd_quantiles[1]} 95%={deg_sd_quantiles[2]}")) + 
    geom_vline(xintercept = deg_sd_quantiles)
  
  kappa_plot <- ggplot(prior_sim, aes(x = kappa)) + 
    geom_histogram() + geom_rug()
  
  kappa_trunc_plot <- ggplot(prior_sim, aes(x = kappa)) + 
    geom_histogram(binwidth = 0.01) + 
    geom_rug() + 
    xlim(0,10) + 
    labs(x="kappa zoomed")
  
  
  quantiles <- quantile(prior_sim$sim_data,c(0.025, 0.975))
  quantile_round <- round(quantiles, 2)
  
  sim_data <- ggplot(prior_sim, aes(x = sim_data)) + 
    geom_histogram(binwidth=2) + 
    geom_vline(xintercept = quantiles) + 
    labs(subtitle = glue("2.5% and 97.5% quantile lines -- {quantile_round[1]} , {quantile_round[2]}"), x = "prior_implied errors (degrees)")
  
  cowplot::plot_grid(deg_sd, kappa_plot, kappa_trunc_plot,  sim_data, ncol = 1)
  
}

sample_gamma <- function(mean, mult_fact){
  
  shape1 <- mean * mult_fact
  shape2 <- mult_fact
  
  res <- enframe(rgamma(1e5, shape1, shape2), name = NULL, value = "sim")
  sim_mean <- round(mean(res$sim), 2)
  sim_var <- round(stats::var(res$sim), 2)
  quantile_line <- round(quantile(res$sim, c(0.05, 0.95)), 2)

  ggplot(res, aes(x = sim)) + 
    geom_density() + 
    geom_rug() + 
    labs(subtitle = glue("gamma({shape1}, {shape2})\nmean = {sim_mean}, var = {sim_var}, 5%-quantile = {quantile_line[1]}, 95% = {quantile_line[2]}")) + 
    geom_vline(xintercept = quantile_line) +
    xlim(0, 200) + 
    theme(plot.subtitle = element_text( size = 10))
  
}

```

## Normal

```{r fig.height=10}

prior_sd <- 100
prior_sim <- abs(rnorm(5e4, 0, prior_sd))
title_str <- paste0("halfNormal(0, ", prior_sd, ")")

plot_prior_dist(prior_sim, title_str)

```


## Exponential

```{r fig.height=10}

desired_mean <- 100
prior_lambda <- 1/desired_mean
prior_sim <- rexp(5e4, prior_lambda)
title_str <- paste0("exp(", prior_lambda, ")")

plot_prior_dist(prior_sim, title_str)

```


### Gamma

```{r fig.height=15, fig.width=10}

gamma_sim <- tibble("mean" = 60, mult_fact = c(1/32, 1/25, 1/20, 1/16, 1/8, 1/4, 1/2, 1)) %>%
  mutate(dens_plot = map2(mean, mult_fact, sample_gamma))

plot_grid(plotlist = gamma_sim$dens_plot, ncol = 2)

```


```{r fig.height=10}

mean <- 60
shape1 <- mean*(1/10)
shape2 <- 1/10
prior_sim <- rgamma(5e4, shape1, shape2)
title_str <- paste0("gamma(", shape1, ",", shape2, ")")

plot_prior_dist(prior_sim, title_str)

```

##### Extreme kappa values are far less likely with a gamma distribution


## Expanded logit link

```{r}
exp_sim <- tibble("orig" = seq(-1e2, 1e2)) %>%
  mutate(inv_logit_trans = exp(orig)/(1 + exp(orig)), inv_logit_trans5 = exp(orig)/(1 + exp(orig))*5) 

ggplot(exp_sim, aes(x = orig, y = inv_logit_trans5)) + 
  geom_point()
```


## Log link function


Plot exp function
```{r}

exp_sim <- tibble("orig" = seq(-1e2, 1e2)) %>%
  mutate(exp_trans = exp(orig)) 

ggplot(exp_sim, aes(x = orig, y = exp_trans)) + 
  geom_point() + 
  ylim(0,10)
```


```{r fig.height=10}

mean <- 60
shape1 <- mean*(1/10)
shape2 <- 1/10
prior_sim <- exp(rgamma(5e4, shape1, shape2))
title_str <- paste0("log-gamma(", shape1, ",", shape2, ")")

plot_prior_dist(prior_sim, title_str)

```




